---
title: "退出に関する pooled logit QMLE DiD 推定図"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
  pdf_document:
    toc: true
    keep_tex: true
#    fig_caption: yes
---


```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # パッケージ読込時などのメッセージを表示しない
                      warning=FALSE) # 警告メッセージを表示しない

```

# パッケージの読み込み
```{r package}
library(tidyverse)
library(fixest)
library(etwfe)
library(modelsummary)
```


# データの読み込み
```{r data}
aff_eu <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_eu_sample.dta")

aff_highEU <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_high_income_eu_sample.dta")



# Restrict years between 2010 and 2020
aff_eu <- aff_eu %>%             filter(year >= 2010 & year <= 2020)
aff_highEU <- aff_highEU %>%     filter(year >= 2010 & year <= 2020)



```






# Logitモデル

## Exit-Logit with `fixest`

- The number of observation reduced significantly.
- It does not converge. 
- Too many fixed effects prevent the model from converging.
- Incidental parameters problem occurs.


```

es3 <- tryCatch(
  fixest::feglm(
    exitit ~ i(year, GBR, 2014) | year + AffiliateCode,
    data = aff_eu,
    family = "logit",
    vcov = ~ country
  ),
  error = function(e) NULL
)

es4 <- tryCatch(
  fixest::feglm(
    exitit ~ i(year, GBR, 2014) | year + AffiliateCode,
    data = aff_highEU,
    family = "logit",
    vcov = ~ country
  ),
  error = function(e) NULL
)

if (!is.null(es3) && !is.null(es4)) {
  fixest::etable(es3)
  fixest::etable(es4)

  es3_n = as.numeric(es3[["nobs"]])
  es4_n = as.numeric(es4[["nobs"]])
  legend3 <- paste("EU (N = ", es3_n, ")")
  legend4 <- paste("High income EU (N =", es4_n, ")")

  iplot(list(es3, es4), pt.join = TRUE,
        main = "Effect of the Brexit referendum on exit probability",
        sub = "Affiliate-level balanced panel",
        xlab = "Logit model"
        )
  legend("topleft", col = 1:2, pch = 10, cex = 0.7, lwd = 1, lty = 1:2,
         legend = c(legend3, legend4),
         title = "Comparison countries")
} else {
  plot.new()
  text(0.5, 0.5, "TWFE logit model could not be estimated in this sample.")
}

```




## Pooled logit QMLE DiD with `etwfe`

- Following \citet{wooldridge2023simple}, we use a pooled logit QMLE DiD specification for the binary exit outcome.
- The `etwfe` package implements the nonlinear pooled specification with group-level treatment timing.
- This nonlinear specification is analogous to the linear ETWFE setup, but we avoid calling it "ETWFE logit" in the paper to keep the terminology consistent.
  



### High income EU {-}

```{r}
es8logit <- etwfe::etwfe(exitit ~  1  ,
               tvar = year, # time var
               gvar = first_year, # group var
               #xvar = N_Aff_EU  ,
               ivar =  year + AffiliateCode, # FEs
               data = aff_highEU,
               family = "logit",
               vcov = ~country)
fixest::etable(es8logit)


# イベントスタディ係数と標準誤差を抽出
coef_vec <- coef(es8logit)
se_vec <- sqrt(diag(vcov(es8logit)))
event_terms <- grep("^\\.Dtreat:first_year::2016:year::20(16|18|20)$",
                    names(coef_vec),
                    value = TRUE)

es8Logit_results <- data.frame(
  term = event_terms,
  event = as.integer(sub(".*year::", "", event_terms)),
  estimate = unname(coef_vec[event_terms]),
  std.error = unname(se_vec[event_terms])
)
es8Logit_results$conf.low <- es8Logit_results$estimate - 1.96 * es8Logit_results$std.error
es8Logit_results$conf.high <- es8Logit_results$estimate + 1.96 * es8Logit_results$std.error

```



### Estimation tables {-}

```{r}
# 推定結果の係数名を表示用に整える
rename_fn = function(old_names) {
  new_names = gsub(".Dtreat", "Year =", old_names)
  setNames(new_names, old_names)
}

models <- list(
               "Logit" = es8logit)

modelsummary(
  models, 
  shape       = term:event:statistic ~ model, 
  coef_rename = rename_fn, # rename
  coef_omit = ".*N_Aff*", 
  gof_omit    = "Adj|Within|IC|RMSE", 
  stars = c('*' = 0.05, '**' = 0.01, '***' = 0.001) ,
  title       = "Event study (pooled logit QMLE DiD)", 
  notes       = "Std. errors are clustered at the county level" 
)


```


### Event study plot

```{r Fig6-ETWFE-exit-logit, dpi = 300}
# イベントスタディ図
# Add event to + 2016
es8Logit_results$event <- es8Logit_results$event

n_obs <- es8logit[["nobs"]]
r2 <- es8logit[["pseudo_r2"]]
label_caption <- paste0("Pooled logit QMLE DiD specification. Affiliate-level balanced panel. N = ", n_obs, ", Pseudo R2 = ", round(r2, 3), ".")

# Plot the estimate
p_etwfe_logit <- ggplot(es8Logit_results, aes(x = event, y = estimate)) +
  geom_hline(yintercept = 0) +
  scale_x_continuous(breaks = c(2016, 2018, 2020)) +
  labs(x = "Year (two-year intervals)", 
       y = "Effect of the Brexit referendum",
       title = "Effects of the Brexit referendum on exit probability",
       caption = label_caption
       ) +
  theme_minimal() +
  theme(legend.position = "top") +
  geom_text(aes(label = round(estimate, 3)), 
            vjust = -0.5, hjust = 0.5, size = 3)

p_etwfe_logit <- p_etwfe_logit +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high))

p_etwfe_logit

ggsave("../../04_tex/main/Fig6.eps", dpi = 300)
```



## プレトレンド検定

### All observations {-}


```{r event-study-test1, dpi = 300}
# 事前係数をまとめたプレトレンド検定

es10 <- fixest::feglm(exitit ~ 1+ i(year, GBR, 2014) 
                       | year + GBR, 
               data = aff_highEU,
               #family = binomial(link = "logit"),
               family = "logit",
               vcov = ~ country)
fixest::etable(es10)

fixest::iplot(es10, pt.join = TRUE,
      main = "Effect of the Brexit referendum on exit probability",
      sub = "Affiliate-level balanced panel",
      xlab = "Logit model"
      )
```


### Not-yet treated observations {-}

```{r event-study-test2, dpi = 300}
# Subset of year <=2014
aff_highEU_pre2014 <- aff_highEU %>% filter(year <= 2014)

# Fixed effects & Interaction terms
aff_highEU_pre2014$year2010 <- ifelse(aff_highEU_pre2014$year == 2010, 1, 0)
aff_highEU_pre2014$year2012 <- ifelse(aff_highEU_pre2014$year == 2012, 1, 0)
aff_highEU_pre2014$year2014 <- ifelse(aff_highEU_pre2014$year == 2014, 1, 0)
aff_highEU_pre2014$year2010GBR <- aff_highEU_pre2014$year2010 * aff_highEU_pre2014$GBR
aff_highEU_pre2014$year2012GBR <- aff_highEU_pre2014$year2012 * aff_highEU_pre2014$GBR
aff_highEU_pre2014$year2014GBR <- aff_highEU_pre2014$year2014 * aff_highEU_pre2014$GBR


es11 <- fixest::feglm(exitit ~  year2010GBR + year2012GBR + year2014GBR
                       | year , 
               data = aff_highEU_pre2014,
               #family = binomial(link = "logit"),
               family = "logit",
               vcov = ~ country)
fixest::etable(es11)

# Joint Wald test of the coefficients
# https://lrberge.github.io/fixest/reference/wald.html#ref-examples
fixest::wald(es11, 
             keep = "year201[[:digit:]]GBR", # Regular expression
             print = TRUE)

# Coefplot 
fixest::coefplot(es11, 
                 keep = "year201[[:digit:]]GBR",
                 main = "Event study test",
                 sub = "Affiliate-level balanced panel",
                 xlab = "Logit model"
                 )
```




# References {-}

- [Create a publication-ready LaTeX regression table with `kableExtra` in R](https://tilburgsciencehub.com/topics/visualization/reporting-tables/reportingtables/kableextra/)

- [modelsummary: regression tables](https://modelsummary.com/articles/modelsummary.html)

- [fixest: Exporting estimation tables](https://lrberge.github.io/fixest/articles/exporting_tables.html#exporting-multiple-estimations-to-latex)


For fixest:
- [Fast Fixed-Effects Estimation: Short Introduction](https://cran.r-project.org/web/packages/fixest/vignettes/fixest_walkthrough.html)

For OLS:
- [Fixed-effects OLS estimations](https://lrberge.github.io/fixest/reference/feols.html)

For Logit model:
- [Fixed-effects GLM estimations](https://lrberge.github.io/fixest/reference/feglm.html)
- [family: Family Objects for Models](https://rdrr.io/r/stats/family.html)
- [LOGIT REGRESSION | R DATA ANALYSIS EXAMPLES](https://stats.oarc.ucla.edu/r/dae/logit-regression/)
