---
title: "Appendix G. Affiliate-Level Exit Responses by the Number of UK Affiliates within Parent Firms"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This temporary note examines whether affiliate-level exit responses to the
Brexit referendum differed between affiliates whose parent firms had only one
UK affiliate in 2010 and affiliates whose parent firms had two or more UK
affiliates in 2010.

The key idea is that parent firms with multiple UK affiliates may have more
scope to reorganize within the UK after the referendum, for example by closing
one affiliate while keeping other UK affiliates in place.

# Caveat

This is a reduced-form heterogeneity exercise at the affiliate level. It does
not directly observe whether resources from a closed affiliate were actually
reallocated to other surviving UK affiliates within the same parent firm.

```{r packages}
library(rio)
library(dplyr)
library(tidyr)
library(fixest)
library(knitr)
library(ggplot2)
```

# Parent-level UK affiliate counts in 2010

```{r parent-uk-count}
# 親子関係を含む affiliate-level パネルデータを読み込む
parent_panel <- import("../../03_data_output/Affiliate/affiliate_panel_with_parent_links.dta") %>%
  filter(year == 2010)

# 2010 年時点での親企業ごとの UK affiliate 数を作る
parent_uk_count_2010 <- parent_panel %>%
  group_by(JPCode) %>%
  summarise(
    total_affiliates_2010 = n_distinct(AffiliateCode),
    uk_affiliates_2010 = n_distinct(AffiliateCode[iso == "GBR"]),
    any_uk_presence_2010 = uk_affiliates_2010 > 0,
    uk_multi_affiliate_group = case_when(
      uk_affiliates_2010 == 0 ~ "No UK affiliates",
      uk_affiliates_2010 == 1 ~ "One UK affiliate",
      uk_affiliates_2010 >= 2 ~ "Two or more UK affiliates",
      TRUE ~ NA_character_
    ),
    .groups = "drop"
  )

parent_uk_count_2010
```

# Baseline exit sample

```{r exit-sample}
# baseline の high-income EU exit sample を読み込む
exit_sample <- import("../../03_data_output/Affiliate/affiliate_panel_brexit_high_income_eu_sample.dta") %>%
  filter(year >= 2010, year <= 2020) %>%
  left_join(parent_uk_count_2010, by = "JPCode")

# exit sample の affiliate 数・親企業数などを確認する
exit_sample %>%
  summarise(
    affiliates = n_distinct(AffiliateCode),
    parents = n_distinct(JPCode),
    parents_with_uk_presence = n_distinct(JPCode[any_uk_presence_2010]),
    parents_with_multiple_uk_affiliates = n_distinct(JPCode[uk_affiliates_2010 >= 2])
  )
```

# Sample composition

```{r sample-composition}
sample_composition <- exit_sample %>%
  group_by(uk_multi_affiliate_group) %>%
  summarise(
    parents = n_distinct(JPCode),
    affiliates = n_distinct(AffiliateCode),
    observations = n(),
    .groups = "drop"
  )

sample_composition %>%
  kable(caption = "Composition of the baseline exit sample by the number of UK affiliates within each parent firm")
```

# Summary for the paper

```{r paper-summary-values, include=FALSE}
one_parents <- sample_composition %>%
  filter(uk_multi_affiliate_group == "One UK affiliate") %>%
  pull(parents)

one_affiliates <- sample_composition %>%
  filter(uk_multi_affiliate_group == "One UK affiliate") %>%
  pull(affiliates)

one_observations <- sample_composition %>%
  filter(uk_multi_affiliate_group == "One UK affiliate") %>%
  pull(observations)

multi_parents <- sample_composition %>%
  filter(uk_multi_affiliate_group == "Two or more UK affiliates") %>%
  pull(parents)

multi_affiliates <- sample_composition %>%
  filter(uk_multi_affiliate_group == "Two or more UK affiliates") %>%
  pull(affiliates)

multi_observations <- sample_composition %>%
  filter(uk_multi_affiliate_group == "Two or more UK affiliates") %>%
  pull(observations)

no_uk_parents <- sample_composition %>%
  filter(uk_multi_affiliate_group == "No UK affiliates") %>%
  pull(parents)

no_uk_affiliates <- sample_composition %>%
  filter(uk_multi_affiliate_group == "No UK affiliates") %>%
  pull(affiliates)

no_uk_observations <- sample_composition %>%
  filter(uk_multi_affiliate_group == "No UK affiliates") %>%
  pull(observations)

parents_with_multiple_uk_affiliates <- exit_sample %>%
  summarise(value = n_distinct(JPCode[uk_affiliates_2010 >= 2])) %>%
  pull(value)

parents_with_any_uk_presence <- exit_sample %>%
  summarise(value = n_distinct(JPCode[any_uk_presence_2010])) %>%
  pull(value)
```

In the baseline exit sample, `r parents_with_any_uk_presence` parent firms have
at least one UK affiliate in 2010. Among them, `r parents_with_multiple_uk_affiliates`
parent firms have two or more UK affiliates. The group of parents with one UK
affiliate contains `r one_parents` parent firms, `r one_affiliates` affiliates,
and `r one_observations` affiliate-year observations. The group of parents with
two or more UK affiliates contains `r multi_parents` parent firms,
`r multi_affiliates` affiliates, and `r multi_observations` affiliate-year
observations. For comparison, the group of parents with no UK affiliates
contains `r no_uk_parents` parent firms, `r no_uk_affiliates` affiliates, and
`r no_uk_observations` affiliate-year observations.

# Distribution of UK affiliate counts

```{r distribution}
parent_uk_count_dist <- exit_sample %>%
  distinct(JPCode, uk_affiliates_2010, uk_multi_affiliate_group)

ggplot(
  parent_uk_count_dist %>% filter(uk_affiliates_2010 > 0),
  aes(x = uk_affiliates_2010)
) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "#6baed6", color = "white") +
  scale_x_continuous(breaks = seq(1, max(parent_uk_count_dist$uk_affiliates_2010, na.rm = TRUE), by = 1)) +
  labs(
    x = "Number of UK affiliates in 2010",
    y = "Number of parent firms",
    title = "Distribution of parent-level UK affiliate counts in 2010",
    subtitle = "Histogram restricted to parent firms with at least one UK affiliate"
  ) +
  theme_minimal(base_size = 12)
```

# Event-study estimates by the number of UK affiliates

```{r event-study}
event_groups <- c("One UK affiliate", "Two or more UK affiliates")

event_parent_counts <- sample_composition %>%
  filter(uk_multi_affiliate_group %in% event_groups) %>%
  mutate(uk_multi_affiliate_group = factor(uk_multi_affiliate_group, levels = event_groups)) %>%
  arrange(uk_multi_affiliate_group)

event_samples <- split(
  exit_sample %>% filter(uk_multi_affiliate_group %in% event_groups),
  factor(
    exit_sample %>% filter(uk_multi_affiliate_group %in% event_groups) %>% pull(uk_multi_affiliate_group),
    levels = event_groups
  )
)

event_models <- lapply(
  event_samples,
  function(df) {
    feols(
      exitit ~ i(year, GBR, 2014) | year + AffiliateCode,
      data = df,
      vcov = ~country
    )
  }
)

extract_event_years <- function(model) {
  coef_names <- names(coef(model))
  as.numeric(sub(".*year::([0-9]{4}):GBR.*", "\\1", coef_names))
}

joint_test_pvalue <- function(model, years) {
  coef_names <- names(coef(model))
  test_terms <- coef_names[extract_event_years(model) %in% years]

  if (length(test_terms) == 0) {
    return(NA_real_)
  }

  b <- coef(model)[test_terms]
  V <- vcov(model)[test_terms, test_terms, drop = FALSE]
  V_inv_b <- tryCatch(
    solve(V, b),
    error = function(e) qr.solve(V, b)
  )
  wald_stat <- as.numeric(t(b) %*% V_inv_b)
  1 - pchisq(wald_stat, df = length(test_terms))
}

event_fit_stats <- tibble(
  uk_multi_affiliate_group = factor(names(event_models), levels = event_groups),
  N = sapply(event_models, nobs),
  pretrend_p = sapply(event_models, joint_test_pvalue, years = c(2010, 2012)),
  post_p = sapply(event_models, joint_test_pvalue, years = c(2016, 2018, 2020))
) %>%
  left_join(event_parent_counts, by = "uk_multi_affiliate_group") %>%
  arrange(uk_multi_affiliate_group)

etable(
  event_models,
  keep = "%year::2010:GBR|year::2012:GBR|year::2016:GBR|year::2018:GBR|year::2020:GBR",
  fitstat = ~ n + wr2,
  tex = FALSE
)

event_test_results <- event_fit_stats %>%
  transmute(
    `Group` = as.character(uk_multi_affiliate_group),
    `Pre-trend test p-value` = round(pretrend_p, 3),
    `Post-treatment joint test p-value` = round(post_p, 3)
  )

kable(
  event_test_results,
  caption = "Joint tests for pre-trends and post-treatment effects by the number of UK affiliates within each parent firm"
)
```

# Event-study plot

```{r event-study-plot}
legend_labels <- as.character(event_fit_stats$uk_multi_affiliate_group)

note_line_one <- sprintf(
  "One UK affiliate: N = %s, Parent firms = %s, Affiliates = %s, Observations = %s.",
  event_fit_stats$N[event_fit_stats$uk_multi_affiliate_group == "One UK affiliate"],
  event_fit_stats$parents[event_fit_stats$uk_multi_affiliate_group == "One UK affiliate"],
  event_fit_stats$affiliates[event_fit_stats$uk_multi_affiliate_group == "One UK affiliate"],
  event_fit_stats$observations[event_fit_stats$uk_multi_affiliate_group == "One UK affiliate"]
)

note_line_multi <- sprintf(
  "Two or more UK affiliates: N = %s, Parent firms = %s, Affiliates = %s, Observations = %s.",
  event_fit_stats$N[event_fit_stats$uk_multi_affiliate_group == "Two or more UK affiliates"],
  event_fit_stats$parents[event_fit_stats$uk_multi_affiliate_group == "Two or more UK affiliates"],
  event_fit_stats$affiliates[event_fit_stats$uk_multi_affiliate_group == "Two or more UK affiliates"],
  event_fit_stats$observations[event_fit_stats$uk_multi_affiliate_group == "Two or more UK affiliates"]
)

plot_event_study <- function() {
  do.call(
    iplot,
    c(
      event_models,
      list(
        pt.join = TRUE,
        sep = 0.5,
        ref.line = 0,
        xlab = "Year (two-year intervals)",
        ylab = "Estimated effect on exit probability",
        main = "Affiliate-Level Exit Responses by the Number of UK Affiliates within Parent Firms",
        ci_level = 0.95,
        col = c("#1b9e77", "#d95f02"),
        pt.col = c("#1b9e77", "#d95f02")
      )
    )
  )

  legend(
    "topright",
    legend = legend_labels,
    col = c("#1b9e77", "#d95f02"),
    pch = 19,
    lty = 1:2,
    lwd = 1,
    bty = "n",
    title = "Parent UK-affiliate group"
  )
}

plot_event_study()

postscript(
  "../../04_tex/main/FigG3.eps",
  horizontal = FALSE,
  width = 8,
  height = 6
)
plot_event_study()
dev.off()
```

```{r event-study-note, results='asis'}
cat(
  paste0(
    "**Figure note.** ",
    note_line_one,
    "<br>",
    note_line_multi
  )
)
```

# Interpretation

This note is intended as a feasibility check. If affiliates belonging to parent
firms with multiple UK affiliates show a larger exit response, one possible
interpretation is that parent firms may have had more scope to reorganize
within the UK while preserving some UK presence.
