---
title: "Japan's Share of Inward FDI Stocks in the United Kingdom"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This temporary note calculates Japan's share of inward FDI stocks in the United
Kingdom using the UIFS4 bilateral inward FDI stock data.

The FDI stock values are interpreted as million USD, following Kox (2025).
Missing bilateral cells are not interpreted as zeros; the denominator below is
the sum of numerical UK inward FDI stock cells reported in the UIFS4 file for a
given year.

The calculation is:

\[
\text{Japan share}_{t}
= \frac{\text{inward FDI stock in GBR from JPN}_{t}}
{\sum_p \text{inward FDI stock in GBR from partner } p_{t}}
\times 100.
\]

# Packages

```{r packages}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)
```

# Input data

```{r inputs}
fdi_path <- "../../02_data_input/Kox_UIFS4_bilat_inw_FDI_stocks_2001_2022.csv"
geo_path <- "../../02_data_input/Standardised_geo_identifiers_UIFS4_database_v10.csv"

fdi <- read_delim(fdi_path, delim = "|", show_col_types = FALSE)
geo <- read_delim(geo_path, delim = "|", show_col_types = FALSE)
```

# Country codes

```{r country-codes}
country_codes <- geo %>%
  filter(iso3 %in% c("GBR", "JPN")) %>%
  select(iso3, ctry_name, region, continent)

kable(country_codes)
```

# Calculation

```{r calculate-share}
uk_inward <- fdi %>%
  filter(iso3_r == "GBR")

uk_inward_total <- uk_inward %>%
  group_by(year) %>%
  summarise(
    uk_inward_fdi_total = sum(inw_fdi_stock, na.rm = TRUE),
    n_source_countries = n_distinct(iso3_p),
    n_nonmissing_sources = sum(!is.na(inw_fdi_stock)),
    .groups = "drop"
  )

uk_inward_from_japan <- uk_inward %>%
  filter(iso3_p == "JPN") %>%
  transmute(
    year,
    uk_inward_fdi_from_japan = inw_fdi_stock
  )

uk_japan_share <- uk_inward_total %>%
  left_join(uk_inward_from_japan, by = "year") %>%
  mutate(
    japan_share = uk_inward_fdi_from_japan / uk_inward_fdi_total,
    japan_share_percent = 100 * japan_share
  ) %>%
  arrange(year)
```

# Top Source Countries by Year

```{r top-source-countries}
non_country_codes <- c("WLD", "WLG", "XLG")

uk_inward_ranking <- uk_inward %>%
  filter(
    !is.na(inw_fdi_stock),
    inw_fdi_stock > 0,
    !iso3_p %in% c("GBR", non_country_codes)
  ) %>%
  left_join(
    geo %>% select(iso3, source_country = ctry_name),
    by = c("iso3_p" = "iso3")
  ) %>%
  group_by(year) %>%
  arrange(desc(inw_fdi_stock), .by_group = TRUE) %>%
  mutate(rank = row_number()) %>%
  ungroup() %>%
  select(
    year,
    rank,
    iso3_p,
    source_country,
    uk_inward_fdi_stock = inw_fdi_stock
  )

uk_inward_ranking %>%
  filter(rank <= 10) %>%
  mutate(uk_inward_fdi_stock = round(uk_inward_fdi_stock, 2)) %>%
  kable(
    col.names = c(
      "Year",
      "Rank",
      "Source ISO3",
      "Source country",
      "UK inward FDI stock (million USD)"
    )
  )
```

# Result

```{r result-table}
uk_japan_share %>%
  mutate(
    uk_inward_fdi_total = round(uk_inward_fdi_total, 2),
    uk_inward_fdi_from_japan = round(uk_inward_fdi_from_japan, 2),
    japan_share_percent = round(japan_share_percent, 2)
  ) %>%
  select(
    year,
    uk_inward_fdi_total,
    uk_inward_fdi_from_japan,
    japan_share_percent,
    n_nonmissing_sources
  ) %>%
  kable(
    col.names = c(
      "Year",
      "UK inward FDI total (million USD)",
      "UK inward FDI from Japan (million USD)",
      "Japan share (%)",
      "Non-missing source countries"
    )
  )
```

# Plot

```{r plot-share, fig.width=7, fig.height=4}
ggplot(uk_japan_share, aes(x = year, y = japan_share)) +
  geom_line(linewidth = 0.8, color = "#2B6CB0") +
  geom_point(size = 1.8, color = "#2B6CB0") +
  scale_x_continuous(breaks = seq(2001, 2022, by = 3)) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(
    x = NULL,
    y = "Japan's share of UK inward FDI stocks",
    title = "Japan's Share of Inward FDI Stocks in the United Kingdom"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold")
  )
```

# FDI Stock Trends

```{r plot-fdi-stocks, fig.width=7, fig.height=5}
p_fdi_stocks <- uk_japan_share %>%
  select(
    year,
    `UK inward FDI total` = uk_inward_fdi_total,
    `UK inward FDI from Japan` = uk_inward_fdi_from_japan
  ) %>%
  pivot_longer(
    cols = -year,
    names_to = "series",
    values_to = "fdi_stock"
  ) %>%
  ggplot(aes(x = year, y = fdi_stock, color = series)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.8) +
  facet_wrap(~series, ncol = 1, scales = "free_y") +
  scale_x_continuous(breaks = seq(2001, 2022, by = 3)) +
  scale_y_continuous(labels = comma) +
  scale_color_manual(
    values = c(
      "UK inward FDI total" = "#2B6CB0",
      "UK inward FDI from Japan" = "#C05621"
    )
  ) +
  labs(
    x = NULL,
    y = "Inward FDI stock (million USD)",
    title = "UK Inward FDI Stocks: Total and From Japan"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold"),
    plot.title = element_text(face = "bold")
  )

p_fdi_stocks

ggsave(
  "../../04_tex/oa/FigX6.eps",
  p_fdi_stocks,
  device = cairo_ps,
  width = 7,
  height = 5,
  dpi = 300
)
```

# Latest year

```{r latest-year}
uk_japan_share %>%
  filter(year == max(year, na.rm = TRUE)) %>%
  mutate(
    uk_inward_fdi_total = round(uk_inward_fdi_total, 2),
    uk_inward_fdi_from_japan = round(uk_inward_fdi_from_japan, 2),
    japan_share_percent = round(japan_share_percent, 2)
  ) %>%
  select(year, uk_inward_fdi_total, uk_inward_fdi_from_japan, japan_share_percent) %>%
  kable(
    col.names = c(
      "Year",
      "UK inward FDI total (million USD)",
      "UK inward FDI from Japan (million USD)",
      "Japan share (%)"
    )
  )
```
