---
title: "現地法人退出の生存分析"
author: "Ayumu Tanaka"
date: "2024-05-24"
#   pdf_document: 
#     latex_engine: xelatex 
# documentclass: bxjsarticle
# classoption: xelatex,ja=standard
# geometry: no
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # cache results
                      message=FALSE, # パッケージ読込時などのメッセージを表示しない
                      warning=FALSE) # 警告メッセージを表示しない

```



# パッケージの読み込み

```{r load-data-package}
# データの読み込み
library(survival)
library(tidyverse)
library(rio)
library(lubridate)
library(ggsurvfit)
library(gtsummary)
library(tidycmprsk)
library(magick)

library(kableExtra)

# devtools::install_github("zabore/condsurv")
# condsurv is not required for the current appendix outputs.
```


# データの読み込み

```{r load-data}
# データの読み込み
library(rio)
aff_last <- rio::import("../../03_data_output/Affiliate/affiliate_last_observation_panel.dta")

# Remove the observation if GBR is missing
aff_last <- aff_last %>% filter(!is.na(GBR))

# Check the distribution of missing values of Aff_size
barplot(table(is.na(aff_last$Aff_size)),
        main = "Distribution of missing values of Aff_size")

# Replacing the Aff_size with country-year average of Aff_size if Aff_size is missing
aff_last <- aff_last %>% 
  group_by(iso, year) %>% 
  mutate(Aff_size = ifelse(is.na(Aff_size), mean(Aff_size, na.rm = TRUE), Aff_size))



# Check the distribution of missing values of Aff_size
barplot(table(is.na(aff_last$Aff_size)),
        main = "Distribution of missing values of Aff_size")
```



# 生存分析データの整形

- Emily C. Zabor. [Survival Analysis in R](https://www.emilyzabor.com/tutorials/survival_analysis_in_r_tutorial.html)

```{r survival-data}
# Remove colomus if exit is NA
aff_last <- aff_last %>% filter(!is.na(exit))

# Remove colomus if survival_years is NA
aff_last <- aff_last %>% filter(!is.na(survival_years))

# status= 0 if censored==1, status=1 if event==1
aff_last$status <- ifelse(aff_last$censored == 1, 0, 1)

# Calculate the survival years by firm and country iso code
Surv(aff_last$survival_years, aff_last$status)[1:10]

# Kaplan-Meier survival curve
s1 <- survfit(Surv(survival_years, status) ~ 1, data = aff_last)
str(s1)

```


# Kaplan-Meier survival curve 1

```{r Kaplan-Meier1}
# Kaplan-Meier survival curve
plot(s1, xlab = "Years", ylab = "Survival Probability", main = "Kaplan-Meier Curve")
```

# Kaplan-Meier survival curve 2


```{r Kaplan-Meier2}
# Kaplan-Meier survival curve
survfit2(Surv(survival_years, status) ~ 1, data = aff_last) %>% 
  ggsurvfit() +
  labs(
    x = "Years",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval() +
  add_risktable()
```

# Comparison of survival curves

## plot()

- [Comparison of survival curves](https://epirhandbook.com/en/survival-analysis.html#comparison-of-survival-curves)


```{r fig-comparison-KM, dpi= 300}
# Create subsample of EU and GBR
aff_last_eu <- aff_last %>% filter(EU_all == 1)

# create the new survfit object based on GBR
linelistsurv_fit_GBR <-  
  survfit(Surv(survival_years, status) ~ GBR, 
                                 data = aff_last_eu)

# set colors
col_group <- c("blue", "red")

# create plot
plot(
  linelistsurv_fit_GBR,
  col = col_group,
  xlab = "Years",
  ylab = "Survival Probability")

# add legend
legend(
  "topright",
  legend = c("EU affiliates","UK affiliates"),
  col = col_group,
  lty = 1,
  cex = .9,
  bty = "n")

```

## ggplot()

```{r fig-comparison-KM-ggplot, dpi= 300}

# create GBR2 = UK affiliate if GBR==1 and EU affiliate if GBR==0
aff_last_eu$GBR2 <- ifelse(aff_last_eu$GBR == 1, "UK affiliate", "EU affiliate")

km1<- survfit2(Surv(survival_years, status) ~ GBR2, 
                                 data = aff_last_eu)


ggsurvfit(km1) +
  labs(
    x = "Years",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  theme_minimal() 


ggsave("../../04_tex/oa/FigX4.png", dpi = 300, width = 8, height = 6)

```

# Log-ranked test

```{r log-rank-test}
survdiff(Surv(survival_years, status) ~ GBR, data = aff_last_eu)

```


# 生存率の計算

```{r survival-rate}
survfit(Surv(survival_years, status) ~ 1, 
        data = aff_last) %>% 
  tbl_survfit(
    times = 5,
    label_header = "**5-year survival (95% CI)**"
  )


tbl1 <- survfit(Surv(survival_years, status) ~ 1, 
        data = aff_last) %>% 
  tbl_survfit(
    times = c(5, 10, 15, 20),
    label_header = "**{time}-year survival (95% CI)**"
  )


```


## Data of survival rate

```{r survival-rate-data}
# 生存率データ
prob <-  tbl1[["inputs"]][["x"]][[1]][["surv"]]
year <-  tbl1[["inputs"]][["x"]][[1]][["time"]]
surv <- data.frame(year,prob)
```


# Median survival time


```{r median-survival-time}
survfit(Surv(survival_years, status) ~ 1, data = aff_last) %>% 
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  )
```

# Resacling the viariables

```{r}
# Dividing "Ratio", "Government_Effectiveness", "Political_Stability" by 100
aff_last$Ratio <- aff_last$Ratio / 100
#aff_last$Government_Effectiveness <- aff_last$Government_Effectiveness / 100
#aff_last$Political_Stability <- aff_last$Political_Stability / 100
#aff_last$Regulatory_Quality <- aff_last$Regulatory_Quality / 100

```

# Making the subsample

```{r}
# Restricting the European countries: EU_all==1
aff_last_eu <- aff_last %>% filter(EU_all == 1)

```

# Barplot of exit year

```{r barplot_year}
# Barplot of exit year
barplot(table(aff_last_eu$year[aff_last_eu$censored == 0]),
        main = "Year of exit (Censored == 0)",
        xlab = "Year",
        ylab = "Number of affiliates")
```


# Cox proportional hazard model

```{r cox-proportional-hazard-model}

# Cox proportional hazard model without country fixed effects
cox1 <- coxph(Surv(survival_years, status) ~ 
        Brexit + Ratio + Aff_size + GBR 
        + log(GDP_PPP) + log(GDP_per_capita) + log(Dist)
        + factor(Parent_SectorCode) + factor(year),
        data = aff_last)

# Cox proportional hazard model with country fixed effects
cox2 <- coxph(Surv(survival_years, status) ~ 
        Brexit + Ratio + Aff_size 
        + factor(Parent_SectorCode) + factor(year)
        + factor(iso), 
        data = aff_last)

# Cox proportional hazard model without country fixed effects- EU countries
cox3 <- coxph(Surv(survival_years, status) ~ 
        Brexit + Ratio + Aff_size + GBR 
        + log(GDP_PPP) + log(GDP_per_capita) + log(Dist)
        + factor(Parent_SectorCode) + factor(year),
        data = aff_last_eu)

# Cox proportional hazard model with country fixed effects - EU countries
cox4 <- coxph(Surv(survival_years, status) ~ 
        Brexit + Ratio + Aff_size 
        + factor(Parent_SectorCode) + factor(year)
        + factor(iso), 
        data = aff_last_eu)

```


# 推定表の出力

```{r modelsummary-aff}
library(modelsummary)

coef_rename = c("Ratio" = "Ownership ratio", 
                "N_Aff_EU" = "No. of non-UK EU affiliates",
                "Aff_size" = "Affiliate size",
                "log(GDP_PPP)" = "log GDP, PPP",
                "log(GDP_per_capita)" = "log GDP per capita, PPP",
                "Government_Effectiveness" = "Government Effectiveness",
                "Political_Stability" = "Political Stability",
                "Regulatory_Quality" = "Regulatory Quality",
                "log(Dist)" = "log Distance from Japan") 


models <- list(
  "w/o country FEs" = cox1,
  "with country FEs" = cox2,
  "w/o country FEs" = cox3,
  "with country FEs" = cox4)

# add rows
library(tibble)
rows <- tribble(~term,    ~cox1,  ~cox2,    ~cox3,  ~cox4,
                'Fixed Effect: Year',   'YES', 'YES',   'YES', 'YES',
                'Fixed Effect: Sector', 'YES',   'YES', 'YES',   'YES',
                'Fixed Effect: Country', 'NO',   'YES', 'NO',   'YES')
attr(rows, 'position') <- c(15, 16, 17) # position of the above rows

# longnote
longnote <- "Hazard ratios are reported. The Cox proportional hazards model estimates them. Failure event is exit. Variables with hazard ratios greater than 1 are associated with a higher likelihood of exit and shorter survival time. Variables with a hazard ratio smaller than 1 are associated with a lower likelihood of exit and longer survival time. Host countries' fixed effects and year-fixed effects are included in the estimation. Standard errors are presented in blankets."

# kableExtra は html_document 環境では knitr が knitr.table.format を上書きするため
# HTML 出力になってしまい .tex への書き出しが機能しない。
# そのため tinytable (modelsummary v2.0+ のデフォルトバックエンド) の
# ネイティブ API を使って LaTeX テーブルを直接生成・保存する。
library(tinytable)

# 列見出しを (1)-(4) にしたモデルリストを作る。
# group_tt() で World / Europe only のグループヘッダーを上段に追加する。
models_for_tbl <- setNames(models, c("(1)", "(2)", "(3)", "(4)"))

# estimation tables
tbl_TabX1 <- modelsummary(models_for_tbl,
             exponentiate = TRUE,  # exponentiate the coefficients
             stars = c('*' = .05, '**' = .01, '***' = .001),  # add significance stars
             fmt = fmt_sprintf("%.5f"),  # 5 decimal places
             gof_omit = 'DF|Deviance|AIC|BIC|RMSE',
             coef_omit = "Intercept|.*factor",  # omit intercept and factor variables
             coef_rename = coef_rename,
             title = 'Cox regression model at affiliate-level',
             add_rows = rows,
             notes = longnote,
             output = "tinytable"
             ) |>
  group_tt(j = list("World" = 2:3, "Europe only" = 4:5))

tabx1_path <- "../../04_tex/oa/TabX1.tex"
save_tt(tbl_TabX1, output = tabx1_path, overwrite = TRUE)

# Add the LaTeX label used by 04_tex/oa/brexit_OA.tex.
tabx1_tex <- readLines(tabx1_path, warn = FALSE)
tabx1_tex <- gsub(
  "caption={Cox regression model at affiliate-level},",
  "caption={Cox regression model at affiliate-level},\nlabel={tab:modelsummary-aff},",
  tabx1_tex,
  fixed = TRUE
)
writeLines(tabx1_tex, tabx1_path)


# show the results
modelsummary(models, 
             exponentiate = TRUE, # exponentiate the coefficients
             stars = c('*' = .05, '**' = .01, '***' = .001), # add significance stars
             fmt = fmt_sprintf("%.5f"), # 5 decimal places
             gof_omit = 'DF|Deviance|AIC|BIC|RMSE',
             coef_omit = "Intercept|.*factor", # omit the intercept and factor variables
             coef_rename = coef_rename,
             title = 'Cox regression model at affiliate-level', # add a title
             add_rows = rows, # add rows
             output = "kableExtra"
             ) %>% 
    add_header_above(c(" " = 1, "(1)" = 1,  "(2)" = 1, "(3)" = 1,  "(4)" = 1)) %>% 
    add_header_above(c(" " = 1, "World" = 2,  "Europe only" = 2))

```

# Modelplot

## World

```{r fig_modelplot_aff_world}
# 全サンプル
models1 <- list(
  "Model 1: w/o country FEs" = cox1,
  "Model 2: with country FEs" = cox2)

# coeffient plot- world
modelplot(models1, exponentiate = TRUE, 
          coef_rename = coef_rename,
          coef_omit = "Intercept|.*factor")

```

## EU only

```{r fig_modelplot_aff_eu}
# Europe only
models2 <- list(
  "Model 3: w/o country FEs" = cox3,
  "Model 4: with country FEs" = cox4)

# coeffient plot - EU
modelplot(models2, exponentiate = TRUE, 
          coef_rename = coef_rename,
          coef_omit = "Intercept|.*factor")
```
## All

```{r fig_modelplot_aff_all, dpi = 300}
# All
## Only display the Brexit coefficient
coef_map = c("Brexit" = "Brexit")

model_all <- list(
  "Model 1: w/o country FEs" = cox1,
  "Model 2: with country FEs" = cox2,
  "Model 3: w/o country FEs" = cox3,
  "Model 4: with country FEs" = cox4)

modelplot(model_all, 
          coef_map = coef_map,
          exponentiate = TRUE)

ggsave("../../04_tex/oa/FigX5.png", dpi = 300, width = 8, height = 6)
```

# Cox propotional test

- The cox proportional tests produces the errors, presumably because of the correlation between covariates. 

```
# Cox propotional test
cox1_ph_test <- survival::cox.zph(cox1) 
cox1_ph_test

cox2_ph_test <- survival::cox.zph(cox2)
cox2_ph_test

cox3_ph_test <- survival::cox.zph(cox3)
cox3_ph_test

cox4_ph_test <- survival::cox.zph(cox4)
cox4_ph_test

```

Without fixed efffects, we can perform the cox proportional hazard test. The p-values of some variables are less than 0.05, indicating that the proportional hazard assumption is violated.


```{r}
cox10 <- coxph(Surv(survival_years, status) ~ 
        Brexit + Ratio + Aff_size + GBR 
        #+ log(GDP_PPP) + log(GDP_per_capita) + log(Dist)
        ,
        data = aff_last)

modelsummary(cox10, exponentiate = TRUE, stars = c('*' = .05, '**' = .01, '***' = .001))

cox10_ph_test <- survival::cox.zph(cox10) 
cox10_ph_test
```


# References {-}


- Survival analysis of "The Epidemiologist R Handbook", https://epirhandbook.com/en/survival-analysis.html
- Emily C. Zabor. Survival analysis in R, https://www.emilyzabor.com/tutorials/survival_analysis_in_r_tutorial.html
- `modelplot`, https://modelsummary.com/articles/modelplot.html
- `modelsummary`, https://modelsummary.com/articles/modelsummary.html
- `survival` package, https://github.com/therneau/survival
