---
title: "Sample Retention from Restricting to Affiliates Present in 2010"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This temporary note calculates how much of the affiliate sample is retained
when the exit analysis is restricted to affiliates that were already present in
2010.

The goal is to answer the referee's question about the share of firms and
observations that remain in the analysis sample.

# Packages

```{r packages}
library(rio)
library(dplyr)
library(tibble)
library(knitr)
```

# Input data

```{r input-data}
# This panel is upstream of the Brexit estimation samples and still contains the
# full set of affiliate-year observations with country identifiers.
affiliate_panel <- import("../../03_data_output/Affiliate/affiliate_panel_with_country_covariates.dta") %>%
  filter(year >= 2010, year <= 2020)

# High-income EU countries used in the baseline exit analysis.
high_income_eu <- c(
  "AUT", "BEL", "DEU", "DNK", "FIN", "FRA",
  "GBR", "IRL", "ITA", "LUX", "NLD", "SWE"
)
```

# Helper functions

```{r helpers}
calculate_retention <- function(df, sample_name) {
  affiliates_2010 <- df %>%
    filter(year == 2010) %>%
    distinct(AffiliateCode) %>%
    pull(AffiliateCode)

  retained_df <- df %>%
    filter(AffiliateCode %in% affiliates_2010)

  tibble(
    sample = sample_name,
    affiliates_full = n_distinct(df$AffiliateCode),
    affiliates_retained = n_distinct(retained_df$AffiliateCode),
    affiliates_share_retained = n_distinct(retained_df$AffiliateCode) / n_distinct(df$AffiliateCode),
    observations_full = nrow(df),
    observations_retained = nrow(retained_df),
    observations_share_retained = nrow(retained_df) / nrow(df)
  )
}

format_share <- function(x) sprintf("%.1f%%", 100 * x)
```

# Retention by sample

```{r retention-table}
full_sample <- affiliate_panel

eu_sample <- affiliate_panel %>%
  filter(euall == 1)

high_income_eu_sample <- affiliate_panel %>%
  filter(iso %in% high_income_eu)

retention_table <- bind_rows(
  calculate_retention(full_sample, "Full sample"),
  calculate_retention(eu_sample, "EU sample"),
  calculate_retention(high_income_eu_sample, "High-income EU sample")
) %>%
  mutate(
    affiliates_share_retained = format_share(affiliates_share_retained),
    observations_share_retained = format_share(observations_share_retained)
  )

kable(
  retention_table,
  caption = "Share of affiliates and affiliate-year observations retained by restricting the sample to affiliates present in 2010"
)
```

# Notes for interpretation

```{r notes}
retention_table
```

The figures above compare:

- the full 2010--2020 affiliate-year panel in each sample, and
- the retained panel after keeping only affiliates that are already observed in 2010.

This is the sample restriction used for the exit analysis in the main paper.
