---
title: "TWFE・ETWFEによる退出の推定"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---


```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # パッケージ読込時などのメッセージを表示しない
                      warning=FALSE) # 警告メッセージを表示しない

```

# パッケージの読み込み

```{r load-package}
library(tidyverse)
```


# データの読み込み
```{r data}
aff_eu <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_eu_sample.dta")

aff_highEU <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_high_income_eu_sample.dta")

aff_oecd <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_non_eu_oecd_sample.dta")

aff <- rio::import("../../03_data_output/Affiliate/affiliate_panel_brexit_full_sample.dta")


# 2010年から2020年に限定
aff_eu <- aff_eu %>% filter(year >= 2010 & year <= 2020)
aff_highEU <- aff_highEU %>% filter(year >= 2010 & year <= 2020)
aff_oecd <- aff_oecd %>% filter(year >= 2010 & year <= 2020)
aff <- aff %>% filter(year >= 2010 & year <= 2020)

```


# TWFEイベントスタディ
## Exit-OLS with `fixest`


```{r Fig-TWFE-Exit-OLS, dpi = 300}

library(fixest)

twfe_exit_high_income_eu <- fixest::feols(exitit ~   i(year, GBR, 2014) 
                       | year + AffiliateCode, 
               data = aff_highEU,
               vcov = ~ country)
fixest::etable(twfe_exit_high_income_eu)

twfe_exit_eu <- fixest::feols(exitit ~   i(year, GBR, 2014) 
                       | year +  AffiliateCode, 
               data = aff_eu,
               vcov = ~ country)
fixest::etable(twfe_exit_eu)


# labels
twfe_exit_high_income_eu_n = as.numeric(twfe_exit_high_income_eu[["nobs"]])
twfe_exit_eu_n = as.numeric(twfe_exit_eu[["nobs"]])
legend1 <- "High income EU"
legend2 <- "EU"
sample_note <- paste0(
  "Observations: High income EU, N = ", twfe_exit_high_income_eu_n,
  "; EU, N = ", twfe_exit_eu_n
)

# coef
b <- twfe_exit_high_income_eu[["coefficients"]]
# decimal to 3
b <- round(b, 3)
coef_years <- as.numeric(gsub(".*::([0-9]+).*", "\\1", names(b)))
coef_labels <- data.frame(year = coef_years, estimate = as.numeric(b))

iplot(list(twfe_exit_high_income_eu, twfe_exit_eu), pt.join = TRUE,
      main = "Effect of the Brexit referendum on exit probability",
      sub = "Affiliate-level balanced panel",
      xlab = "Linear probability model. Two-year event-study bins."
      ) 
legend("topleft", col = 1:2, pch = 10, cex = 0.7, lwd = 1, lty = 1:2,
       legend = c(legend1, legend2),
       title = "Comparison countries") 
legend("bottomleft", legend = sample_note, bty = "n", cex = 0.7, text.col = "black")
# Add value labels
with(coef_labels, text(year, estimate - 0.01, estimate, cex = 0.7, col = 1))


```


### High-income EU only

```{r Fig3-TWFE-Exit-OLS-HighEU, dpi = 300}

twfe_exit_high_income_eu_r2 <- as.numeric(fixest::fitstat(twfe_exit_high_income_eu, "r2"))

postscript("../../04_tex/main/Fig4.eps", horizontal = FALSE,
           width = 8, height = 6)
fixest::iplot(twfe_exit_high_income_eu, pt.join = TRUE,
      main = "Effect of the Brexit referendum on exit probability",
      sub = paste0(
        "Affiliate-level balanced panel. N = ", twfe_exit_high_income_eu_n,
        ", R2 = ", sprintf("%.3f", twfe_exit_high_income_eu_r2)
      ),
      xlab = "OLS. Two-year event-study bins."
      ) 
legend("topleft", col = 1:2, pch = 10, cex = 0.7, lwd = 1, lty = 1:2,
       legend = c(legend1),
       title = "Comparison countries") 
# Add value labels
with(coef_labels, text(year, estimate - 0.01, estimate, cex = 0.7, col = 1))
 
 dev.off()
```


\newpage

# ETWFEイベントスタディ

## Exit-OLS with `etwfe`

### High income EU

```{r ETWFE-Exit-OLS-HighEU, dpi = 300}

library(etwfe)
etwfe_exit_high_income_eu <- etwfe::etwfe(exitit ~  1  ,
               tvar = year, # time var
               gvar = first_year, # group var
               #xvar = N_Aff_EU  ,
               ivar =  year + AffiliateCode, # FEs
               data = aff_highEU,
               family = "gaussian",
               vcov = ~country)
fixest::etable(etwfe_exit_high_income_eu)

# Marginal effects
# fixest の固定効果つきモデルでは、最近の marginaleffects は
# 標準誤差を伴う event-study 効果をそのまま計算できないことがある。
# ここでは event-study の点推定を得るため、vcov = FALSE を明示する。
etwfe_exit_high_income_eu_me = etwfe::emfx(etwfe_exit_high_income_eu, type = "event", vcov = FALSE)


```

### EU

```{r ETWFE-Exit-OLS-EU, dpi = 300}
library(etwfe)
etwfe_exit_eu <- etwfe::etwfe(exitit ~  1  ,
               tvar = year, # time var
               gvar = first_year, # group var
               #xvar = N_Aff_EU  ,
               ivar =  year + AffiliateCode, # FEs
               data = aff_eu,
               family = "gaussian",
               vcov = ~country)
fixest::etable(etwfe_exit_eu)

# Marginal effects
etwfe_exit_eu_me = etwfe::emfx(etwfe_exit_eu, type = "event", vcov = FALSE)

```








## Combine the event study results with `etwfe`-OLS

```{r Fig-ETWFE-Exit-OLS, dpi = 300}
# Add group variable
etwfe_exit_high_income_eu_me$Control <- "High income EU"
etwfe_exit_eu_me$Control <- "EU"

# Add event to +0.2 for es8me
etwfe_exit_eu_me$event <- etwfe_exit_eu_me$event + 0.1

# Combine the two data frames
es <- rbind(etwfe_exit_high_income_eu_me, etwfe_exit_eu_me)

# value label
es$estimateLabel <- round(es$estimate,3)
es$estimateLabel[es$Control == "EU"] <- ""

# Plot the estimate by group
p_exit_etwfe <- ggplot(es, aes(x = event, y = estimate, col = Control, group = Control)) +
  geom_hline(yintercept = 0) +
  labs(x = "Years post treatment (two-year bins)", 
       y = "Effect of the Brexit referendum",
       title = "Effects of the Brexit referendum on exit probability",
       caption = "ETWFE model. OLS. Affiliate-level balanced panel. Two-year event-study bins."
       ) +
  theme_minimal() +
  theme(legend.position = "top") +
  scale_color_manual(values = c("High income EU" = "darkcyan", "EU" = "darkorange"))  +
  geom_text(aes(label = estimateLabel), 
            vjust = -0.5, size = 3, 
            angle = 45,
            colour = "black",
            show.legend = FALSE)

if (all(c("conf.low", "conf.high") %in% names(es))) {
  p_exit_etwfe <- p_exit_etwfe + geom_pointrange(aes(ymin = conf.low, ymax = conf.high))
} else {
  p_exit_etwfe <- p_exit_etwfe + geom_line() + geom_point()
}

p_exit_etwfe

# Reduce event by 0.1 for es8
etwfe_exit_eu_me$event <- etwfe_exit_eu_me$event - 0.1

```


## 推定表の出力




```{r Table-ETWFE-OLS, dpi = 300}

library(kableExtra)
longnote <- "Notes: Marginal effects from Wooldridge's (2021) extended two-way fixed effects (ETWFE) model are reported in the table. Standard errors are clustered at the country level and presented in parentheses. The data are affiliate-level balanced panel data from the OJC data. The estimation uses data from 2010 to 2020, which are already observed at two-year intervals; the 2014 year indicator is omitted as the reference period. To improve computational efficiency, the estimation employs group-level (i.e., country-level) fixed effects instead of unit-level (i.e., affiliate-level) fixed effects. This estimation strategy follows Wooldridge (2021), which demonstrates the equivalence of group- and unit-level fixed effects in linear models. The R package `etwfe` is used for implementation. * $p<0.05$, ** $p<0.01$, *** $p<0.001$."

post_periods <- c(2016, 2018, 2020)
post_period_labels <- as.character(post_periods)

extract_etwfe_table <- function(model) {
  coef_vec <- coef(model)
  se_vec <- sqrt(diag(vcov(model)))
  coef_names <- paste0(".Dtreat:first_year::2016:year::", post_periods)

  tibble::tibble(
    year = post_periods,
    estimate = unname(coef_vec[coef_names]),
    std_error = unname(se_vec[coef_names])
  )
}

fmt_num <- function(x) sprintf("%.3f", x)
fmt_se <- function(x) paste0("(", sprintf("%.3f", x), ")")

tab_exit_high <- extract_etwfe_table(etwfe_exit_high_income_eu)
tab_exit_eu   <- extract_etwfe_table(etwfe_exit_eu)

row_labels <- c(rbind(
  paste0("UK $\\times$ ", post_period_labels),
  rep("", length(post_periods))
))

table_body <- tibble::tibble(
  Term = row_labels,
  `(1)` = c(rbind(fmt_num(tab_exit_high$estimate), fmt_se(tab_exit_high$std_error))),
  `(2)` = c(rbind(fmt_num(tab_exit_eu$estimate), fmt_se(tab_exit_eu$std_error)))
) %>%
  add_row(
    Term = "Num.Obs.",
    `(1)` = as.character(nobs(etwfe_exit_high_income_eu)),
    `(2)` = as.character(nobs(etwfe_exit_eu))
  ) %>%
  add_row(
    Term = "Group Fixed-Effects",
    `(1)` = "Yes", `(2)` = "Yes"
  ) %>%
  add_row(
    Term = "Year Fixed-Effects",
    `(1)` = "Yes", `(2)` = "Yes"
  ) %>%
  add_row(
    Term = "R2",
    `(1)` = fmt_num(as.numeric(fixest::fitstat(etwfe_exit_high_income_eu, "pr2"))),
    `(2)` = fmt_num(as.numeric(fixest::fitstat(etwfe_exit_eu, "pr2")))
  )

# HTML
tab2_html <- kbl(
  table_body,
  format = "html",
  escape = FALSE,
  caption = "Effect of the Brexit Referendum on Exit Probability (ETWFE, OLS)",
  col.names = c("", "(1)", "(2)")
) |>
  add_header_above(c(" " = 1, "Exit probability" = 2)) |>
  kable_styling(full_width = FALSE, position = "center")

tab2_html

# LaTeX
tab2_latex <- kbl(
  table_body,
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  caption = "Effect of the Brexit Referendum on Exit Probability (ETWFE, OLS)",
  label = "Table-ETWFE-OLS",
  align = "lcc",
  linesep = "",
  col.names = c("", "(1)", "(2)")
) |>
  add_header_above(c(" " = 1, "Exit probability" = 2)) |>
  kable_styling(latex_options = c("hold_position"))

tab2_latex <- as.character(tab2_latex)
tab2_latex <- gsub("\\\\begin\\{table\\}\\[!h\\]", "\\\\begin{table}[!ht]", tab2_latex)
# Manually add the note after tabular to allow page-width wrapping
note_latex <- paste0("\\\\end{tabular}\n\\\\begin{flushleft}\n\\\\footnotesize\n", longnote, "\n\\\\end{flushleft}")
tab2_latex <- gsub("\\\\end\\{tabular\\}", note_latex, tab2_latex)
writeLines(tab2_latex, "../../04_tex/main/Tab2.tex")

```


\newpage

# All OECD countries

```{r Fig-TWFE-Exit-OLS-OECD, dpi = 300}

fixestWorldExitOLS <- fixest::feols(exitit ~   i(year, GBR, 2014)
                       | year + AffiliateCode, 
               data = aff_oecd,
               vcov = ~ country)

fixest::iplot(fixestWorldExitOLS, pt.join = TRUE,
      main = "Effect of the Brexit referendum on exit probability",
      sub = "Affiliate-level balanced panel.",
      xlab = "Linear probability model. Two-year event-study bins. \
      OECD countries excluding EU countries."
      )
```



```{r ETWFE-Exit-OLS-OECD}

etwfeWorldExitOLS <- etwfe::etwfe(exitit ~  1  ,
               tvar = year, # time var
               gvar = first_year, # group var
               ivar =  year + AffiliateCode, # FEs
               data = aff_oecd,
               family = "gaussian",
               vcov = ~country)
etwfeWorldExitOLSME <- etwfe::emfx(etwfeWorldExitOLS, type = "event", vcov = FALSE) 

fixest::etable(etwfeWorldExitOLS)

```



# References {-}

- [Create a publication-ready LaTeX regression table with `kableExtra` in R](https://tilburgsciencehub.com/topics/visualization/reporting-tables/reportingtables/kableextra/)

- [modelsummary: regression tables](https://modelsummary.com/articles/modelsummary.html)

- `fixest`
  - [fixest: Exporting estimation tables](https://lrberge.github.io/fixest/articles/exporting_tables.html#exporting-multiple-estimations-to-latex)
  - [Fast Fixed-Effects Estimation: Short Introduction](https://cran.r-project.org/web/packages/fixest/vignettes/fixest_walkthrough.html)

- For OLS:
  - [Fixed-effects OLS estimations](https://lrberge.github.io/fixest/reference/feols.html)

- For Logit model:
  - [Fixed-effects GLM estimations](https://lrberge.github.io/fixest/reference/feglm.html)
  - [family: Family Objects for Models](https://rdrr.io/r/stats/family.html)
  - [LOGIT REGRESSION | R DATA ANALYSIS EXAMPLES](https://stats.oarc.ucla.edu/r/dae/logit-regression/)

- [HonestDiD](https://github.com/asheshrambachan/HonestDiD)
