---
title: "Brexit分析用の現地法人パネル作成"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
  pdf_document:
    toc: true
    keep_tex: true
#    fig_caption: yes
---


```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # パッケージ読込時などのメッセージを表示しない
                      warning=FALSE) # 警告メッセージを表示しない

```


# データの準備

High-income EU countries are Luxembourg, Ireland, Denmark, Netherlands, Sweden, Austria, Germany, Finland, Belgium, France, United Kingdom, and Italy. The GDP per capita of these countries are as follows:

- Luxembourg: $115,531 LUX
- Ireland: $84,339 IRL
- Denmark: $63,434 DNK
- Netherlands: $62,515 NLD
- Sweden: $59,738 SWE
- Austria: $57,256 AUT
- Germany: $55,682 DEU
- Finland: $55,345 FIN
- Belgium: $54,319 BEL 
- France: $46,133 FRA
- United Kingdom: $45,470 GBR
- Italy: $40,594 ITA

## データの読み込み
```{r load-the-data}
library(tidyverse)
library(rio)
aff = import("../../03_data_output/Affiliate/affiliate_panel_survival_ready.dta")
```


```{r}
# `iso` を `country` に変更
names(aff)[names(aff)=="iso"] = "country"

# 高所得EUダミーを作成
aff$highEU <- ifelse(aff$country %in% 
                       c("AUT", "BEL", "DNK", "FIN", "FRA", 
                         "DEU", "IRL", "ITA", "LUX", 
                         "NLD", "SWE", "GBR"), 1, 0)

# 年×現地法人ごとの親会社数を作成
aff <- aff %>%
  group_by(AffiliateCode, year) %>%
  mutate(N_Parent = n())

# `FA_Sector` を `FASector` に変更
names(aff)[names(aff)=="FA_SectorCode2009"] = "FASector"

# 現地法人従業員数を作成
aff$Aff_size_raw <- aff$Aff_size

# Replacing Aff_size with country-year average if missing
aff <- aff %>%
  group_by(country, year) %>%
  mutate(Aff_size = ifelse(is.na(Aff_size), mean(Aff_size, na.rm = TRUE), Aff_size))

# Replacing N_Aff_EU with N_Aff_EU + 1
aff$N_Aff_EU <- aff$N_Aff_EU + aff$N_Aff_GBR

```


## Reducing the affiliates observations to those owned by the parent firm with the largest ownership ratio

```{r}

## 1. Identify the parent that has the largest ownership ratio "Ratio" by year and AffiliateCode
aff <- aff %>%
  group_by(AffiliateCode, year) %>%
  filter(Ratio == max(Ratio))

## 2. If there are multiple parent firms with the same ownership ratio, then select the first one
aff <- aff %>%
  group_by(AffiliateCode, year) %>%
  filter(row_number() == 1)

## 3. Sort the data by AffiliateCode and year
aff <- aff %>%
  arrange(AffiliateCode, year)
```



## Exit_{it} variable

```{r}
# Sort the data by Affiliatecode and year
aff <- aff %>%
  arrange(AffiliateCode, year)

# 各現地法人の最終年を `exit_year` として作成
aff <- aff %>%
  group_by(AffiliateCode) %>%
  mutate(exit_year = max(year) + 1)

```


## 2010年以降のサンプル作成

2010〜2020年の海外子会社のパネルデータで、2010年に存在していた海外子会社に限定。

```{r}
aff <- aff %>%
  filter(year >= 2010)
aff <- aff %>% 
  group_by(AffiliateCode) %>% 
  mutate(min_year=min(year))

aff <- aff %>% 
  filter(min_year == 2010)
aff$min_year <- NULL

# Remove unnecessary variables: 
aff$N_Parent <- NULL
aff$Political_Stability <- NULL
aff$Government_Effectiveness <- NULL
aff$Regulatory_Quality <- NULL
aff$Rule_of_Law <- NULL
aff$Control_of_Corruption <- NULL
#aff$survival_years <- NULL
aff$DistCode1990 <- NULL
aff$DistCode1995 <- NULL
aff$DistCode2000 <- NULL
aff$Ease_business <- NULL
aff$AbroadOwnRatio <- NULL
aff$AbroadOwnRatio <- NULL
#aff$ParentJPNumber <- NULL
#aff$DispatchedNumber <- NULL
aff$StartDateType <- NULL
aff$StartDate <- NULL

```


## バランスドパネル化

2010年に存在していた海外子会社の2010〜2020年のバランスドパネルデータを作成

```{r affiliate-balanced}
library(plm)
aff <- data.frame(aff) # make into data frame
aff <- plm::make.pbalanced(aff, balance.type = c("fill"), index = c("AffiliateCode", "year"))

```


## FDI目的変数の付与

```{r affiliate-purpose}
# import the POI data
POI <- import("../../02_data_input/POI_wide.dta")

# Combine the affiliate data with the POI data. key: AffiliateCode & year

aff <- aff %>%
  left_join(POI, by = c("AffiliateCode", "year"))

# If the EPFDI is missing, then set it to the other year's EPFDI
aff <- aff %>%
  group_by(AffiliateCode) %>%
  mutate(EPFDI = ifelse(is.na(EPFDI), 
                        first(na.omit(EPFDI)), 
                        EPFDI)) %>%
  ungroup()

# If the EPFDI is still missing, then set it to 0.
aff <- aff %>%
  mutate(EPFDI = ifelse(is.na(EPFDI), 0, EPFDI))

# If the HFDI is missing, then set it to the other year's HFDI
aff <- aff %>%
  group_by(AffiliateCode) %>%
  mutate(HFDI = ifelse(is.na(HFDI), 
                       first(na.omit(HFDI)), 
                       HFDI)) %>%
  ungroup()

# If the HFDI is still missing, then set it to 0.
aff <- aff %>%
  mutate(HFDI = ifelse(is.na(HFDI), 0, HFDI))

```




## 共変量の初期値作成

```{r affiliate-initial-values}
# Sort by AffiliateCode and year
aff <- aff %>% 
  arrange(AffiliateCode, year)

# Replacing Parent_SectorClass, FASector, GDP_per_capita with those of 2010
aff <- aff %>% 
  group_by(AffiliateCode) %>% 
  mutate(Parent_SectorClass = first(Parent_SectorClass),
         FASector = first(FASector),
         FA_SectorClass = first(FA_SectorClass),
         country = first(country),
         EU_all = first(EU_all),
         highEU = first(highEU),
         Aff_size = first(Aff_size),
         Aff_size_raw = first(Aff_size_raw),
         GDP_per_capita = first(GDP_per_capita),
         GDP_PPP = first(GDP_PPP),
         N_Aff_EU = first(N_Aff_EU),
         exit_year = first(exit_year),
         JPCode = first(JPCode),
         ParentJPNumber = first(ParentJPNumber),
         survival_years = first(survival_years),
         EPFDI = first(EPFDI),
         HFDI = first(HFDI),
         GBR = first(GBR),
         Parent_SectorClassNameAlph = first(Parent_SectorClassNameAlph),
         FA_SectorClassNameAlph = first(FA_SectorClassNameAlph)
         )

# keep the above variables + Ratio
aff <- aff %>% 
  select(Ratio, AffiliateCode, year, 
         Parent_SectorClass, FASector, FA_SectorClass, country, 
         EU_all, highEU, Aff_size, Aff_size_raw,
         GDP_per_capita, GDP_PPP, N_Aff_EU, 
         exit_year, JPCode, GBR, EPFDI, HFDI,
         ParentJPNumber, survival_years,
         Parent_SectorClassNameAlph, FA_SectorClassNameAlph)

```


## Brexitダミーの作成
```{r aff-brexit}
# Brexitダミーを作成
aff <- aff %>%
  mutate(Brexit = ifelse(year >= 2016 & country =="GBR", 1, 0))

aff$first_year <- 10000
aff$first_year[aff$country=="GBR"] <- 2016
```

## 退出ダミーの作成

```{r aff-exitit}
# `exitit` を 0 で初期化
## if year < exit_year, exitit = 0, otherwise exitit = 1
aff <- aff %>%
  mutate(exitit = ifelse(year >= exit_year, 1, 0))

# If exitit == 1, replace Ratio with 0
aff <- aff %>%
  mutate(Ratio = ifelse(exitit == 1, 0, Ratio))

# Move the exit_year & exitit after the AffiliateCode, year
aff <- aff %>%
  select(AffiliateCode, year, exit_year, exitit, everything())

aff$exit_year <- NULL

```



## 欧州・高所得EUサブサンプルの作成

```{r aff-subsample}
# 高所得EUサンプルを作成
aff_highEU <- aff %>%
  filter(highEU == 1)

# 欧州サンプルを作成
aff_eu <- aff %>%
  filter(EU_all == 1)

```



## OECD対照群サンプルの作成
```{r}
# Select OECD countries
aff_oecd <- aff %>%
  filter(country %in% c("AUS", "AUT", "BEL", 
                        "CAN", "CHL", "COL", "CZE", 
                        "DNK", "EST", "FIN", "FRA", 
                        "DEU", "GRC", "HUN", 
                        "ISL", "IRL", "ISR", "ITA", 
                        "KOR", "LVA", "LTU", "LUX", 
                        "MEX", "NLD", "NZL", "NOR", 
                        "POL", "PRT", "SVK", "SVN", 
                        "ESP", "SWE", "CHE", "TUR", 
                        "GBR", "USA"))
# Remove EU countries from the OECD countries
aff_oecd <- aff_oecd %>%
  filter(EU_all == 0 | GBR==1)

# List the country in the aff_oecd
unique(aff_oecd$country)

```



## データの保存
```{r save-data}

rio::export(aff, "../../03_data_output/Affiliate/affiliate_panel_brexit_full_sample.dta")

rio::export(aff_highEU, "../../03_data_output/Affiliate/affiliate_panel_brexit_high_income_eu_sample.dta")
rio::export(aff_eu, "../../03_data_output/Affiliate/affiliate_panel_brexit_eu_sample.dta")

rio::export(aff_oecd, "../../03_data_output/Affiliate/affiliate_panel_brexit_non_eu_oecd_sample.dta")


```
