---
title: "Robustness Check for Asset Specificity Heterogeneity"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
# Hide package startup messages and warnings in the rendered report.
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This temporary note checks whether the heterogeneity result by asset specificity
is robust across different comparison groups and estimators.

The main outcome is the affiliate-level exit indicator. We compare:

- High-income EU sample
- EU sample
- Non-EU OECD sample
- Full sample

Within each sample, we split observations into:

- Low asset specificity sectors
- High asset specificity sectors

# Packages

```{r packages}
library(rio)
library(dplyr)
library(purrr)
library(stringr)
library(tibble)
library(fixest)
library(etwfe)
library(knitr)
```

# Input data

```{r inputs}
# Asset-specificity classification by industry.
ppe <- import("../../02_data_input/PPE.dta") %>%
  distinct(OJCIndustryCode, .keep_all = TRUE) %>%
  select(OJCIndustryCode, RecoveryRateHigh)

# Estimation samples used in the main paper.
sample_paths <- c(
  "High-income EU" = "../../03_data_output/affiliate_panel_brexit_high_income_eu_sample.dta",
  "EU" = "../../03_data_output/affiliate_panel_brexit_eu_sample.dta",
  "Non-EU OECD" = "../../03_data_output/affiliate_panel_brexit_non_eu_oecd_sample.dta",
  "Full sample" = "../../03_data_output/affiliate_panel_brexit_full_sample.dta"
)
```

# Helper functions

```{r helpers}
prepare_sample <- function(path) {
  import(path) %>%
    left_join(ppe, by = c("FASector" = "OJCIndustryCode")) %>%
    filter(year >= 2010, year <= 2020, !is.na(RecoveryRateHigh))
}

estimate_twfe_exit <- function(df) {
  feols(
    exitit ~ i(year, GBR, 2014) | year + AffiliateCode,
    data = df,
    vcov = ~country
  )
}

estimate_pooled_logit_exit <- function(df) {
  etwfe(
    exitit ~ 1,
    tvar = year,
    gvar = first_year,
    ivar = year + AffiliateCode,
    data = df,
    family = "logit",
    vcov = ~country
  )
}

extract_event_summary <- function(model, estimator_name) {
  ct <- as.data.frame(coeftable(model))
  ct$term <- rownames(ct)
  rownames(ct) <- NULL

  if (estimator_name == "TWFE OLS") {
    event_rows <- ct %>%
      filter(str_detect(term, "^year::[0-9]{4}:GBR$")) %>%
      mutate(
        event_year = as.integer(str_match(term, "^year::([0-9]{4}):GBR$")[, 2]),
        estimator = estimator_name
      ) %>%
      select(estimator, event_year, estimate = Estimate, std_error = `Std. Error`, statistic = `t value`, p_value = `Pr(>|t|)`)
  } else {
    event_rows <- ct %>%
      filter(str_detect(term, "^\\.Dtreat:first_year::2016:year::20(16|17|18|19|20)$")) %>%
      mutate(
        event_year = as.integer(str_match(term, "year::([0-9]{4})$")[, 2]),
        estimator = estimator_name
      ) %>%
      select(estimator, event_year, estimate = Estimate, std_error = `Std. Error`, statistic = `z value`, p_value = `Pr(>|z|)`)
  }

  event_rows
}

safe_wald_p <- function(model, terms) {
  available <- names(coef(model))
  keep_terms <- terms[terms %in% available]

  if (length(keep_terms) == 0) {
    return(NA_real_)
  }

  restriction <- paste0(keep_terms, " = 0", collapse = " & ")

  out <- tryCatch(
    fixest::wald(model, restriction),
    error = function(e) NULL
  )

  if (is.null(out)) {
    return(NA_real_)
  }

  p_value <- suppressWarnings(as.numeric(out["p"]))

  if (length(p_value) == 0 || is.na(p_value)) {
    return(NA_real_)
  }

  p_value
}

summarize_model <- function(model, estimator_name, sample_name, specificity_name) {
  event_rows <- extract_event_summary(model, estimator_name)

  lookup_p <- function(target_year) {
    value <- event_rows %>%
      filter(event_year == target_year) %>%
      pull(p_value)

    if (length(value) == 0) {
      return(NA_real_)
    }

    value[[1]]
  }

  lookup_coef <- function(target_year) {
    value <- event_rows %>%
      filter(event_year == target_year) %>%
      pull(estimate)

    if (length(value) == 0) {
      return(NA_real_)
    }

    value[[1]]
  }

  tibble(
    sample = sample_name,
    specificity = specificity_name,
    estimator = estimator_name,
    nobs = nobs(model),
    coef_2010 = lookup_coef(2010),
    p_2010 = lookup_p(2010),
    coef_2012 = lookup_coef(2012),
    p_2012 = lookup_p(2012),
    pretrend_p = if (estimator_name == "TWFE OLS") safe_wald_p(model, c("year::2010:GBR", "year::2012:GBR")) else NA_real_,
    post_p = if (estimator_name == "TWFE OLS") safe_wald_p(model, c("year::2016:GBR", "year::2017:GBR", "year::2018:GBR", "year::2019:GBR", "year::2020:GBR")) else NA_real_,
    coef_2016 = lookup_coef(2016),
    p_2016 = lookup_p(2016),
    coef_2019 = lookup_coef(2019),
    p_2019 = lookup_p(2019),
    coef_2020 = lookup_coef(2020),
    p_2020 = lookup_p(2020)
  )
}

run_one_split <- function(df, sample_name, specificity_value, specificity_name) {
  split_df <- df %>% filter(RecoveryRateHigh == specificity_value)

  results <- list()

  twfe_model <- tryCatch(
    estimate_twfe_exit(split_df),
    error = function(e) NULL
  )

  if (!is.null(twfe_model)) {
    results$twfe <- summarize_model(
      model = twfe_model,
      estimator_name = "TWFE OLS",
      sample_name = sample_name,
      specificity_name = specificity_name
    )
  }

  logit_model <- tryCatch(
    estimate_pooled_logit_exit(split_df),
    error = function(e) NULL
  )

  if (!is.null(logit_model)) {
    results$logit <- summarize_model(
      model = logit_model,
      estimator_name = "Pooled logit QMLE DiD",
      sample_name = sample_name,
      specificity_name = specificity_name
    )
  }

  bind_rows(results)
}
```

# Run robustness checks

```{r run-estimation}
robustness_results <- imap_dfr(sample_paths, function(path, sample_name) {
  sample_df <- prepare_sample(path)

  bind_rows(
    run_one_split(sample_df, sample_name, 0, "Low specificity"),
    run_one_split(sample_df, sample_name, 1, "High specificity")
  )
})

robustness_results
```

# Summary table

```{r summary-table}
robustness_results %>%
  mutate(across(where(is.numeric), ~round(.x, 4))) %>%
  kable()
```

# Interpretation guide

The heterogeneity result looks stronger if:

- post-treatment coefficients are more negative or positive for one specificity group
- post-treatment joint p-values remain small across different comparison groups
- pre-trend p-values are not systematically small

The result looks fragile if:

- significance appears only in one comparison group
- pre-trend violations are also strong in the same specification
- the sign changes across samples or estimators
