---
title: "Feasibility Check for Mutually Exclusive Entry and Exit Samples"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This temporary note checks whether we can construct entry and exit analyses based on
mutually exclusive samples, as suggested by the referee.

The proposed logic is:

- Exit sample: affiliates already present in 2010
- Entry sample: affiliates not present in 2010 and first observed after 2010

If this construction is feasible, the entry-side estimate can be interpreted as the
response of "new" affiliates after 2010, which is more directly comparable to the exit
analysis.

# Packages

```{r packages}
library(rio)
library(dplyr)
library(tidyr)
library(fixest)
library(knitr)
```

# Load affiliate-level panel

```{r load-data}
aff <- import("../../03_data_output/affiliate_panel_survival_ready.dta") %>%
  filter(year >= 2010, year <= 2020)

names(aff)[names(aff) == "iso"] <- "country"
```

# Construct mutually exclusive samples

```{r define-samples}
affiliate_timing <- aff %>%
  group_by(AffiliateCode) %>%
  summarise(
    first_observed_year = min(year, na.rm = TRUE),
    first_country = first(country),
    .groups = "drop"
  ) %>%
  mutate(
    exit_sample = first_observed_year == 2010,
    entry_sample = first_observed_year > 2010
  )

table(affiliate_timing$first_observed_year)
```

```{r sample-size}
sample_summary <- affiliate_timing %>%
  summarise(
    affiliates_total = n(),
    affiliates_exit_sample = sum(exit_sample),
    affiliates_entry_sample = sum(entry_sample)
  )

sample_summary %>% kable()
```

# Entry sample by first observed year and country

```{r entry-distribution}
entry_distribution <- affiliate_timing %>%
  filter(entry_sample) %>%
  count(first_observed_year, first_country, sort = TRUE)

entry_distribution %>%
  group_by(first_observed_year) %>%
  summarise(new_affiliates = sum(n), .groups = "drop") %>%
  kable()
```

# Build a country-year panel for "new affiliates after 2010"

```{r build-country-year-entry}
entry_country_year <- affiliate_timing %>%
  filter(entry_sample) %>%
  count(first_country, first_observed_year, name = "new_affiliates") %>%
  rename(country = first_country, year = first_observed_year)

all_country_year <- expand_grid(
  country = sort(unique(aff$country)),
  year = sort(unique(aff$year))
) %>%
  left_join(entry_country_year, by = c("country", "year")) %>%
  mutate(
    new_affiliates = replace_na(new_affiliates, 0L),
    GBR = if_else(country == "GBR", 1L, 0L),
    Brexit = if_else(country == "GBR" & year >= 2016, 1L, 0L)
  )

all_country_year %>%
  group_by(country) %>%
  summarise(total_new_affiliates = sum(new_affiliates), .groups = "drop") %>%
  arrange(desc(total_new_affiliates)) %>%
  head(15) %>%
  kable()
```

# Simple event-study feasibility check

```{r twfe-country-year}
entry_twfe <- feols(
  new_affiliates ~ i(year, GBR, 2014) | country + year,
  data = all_country_year,
  vcov = ~country
)

etable(entry_twfe)
```

# Interpretation

```{r interpretation-table}
entry_event_table <- as.data.frame(coeftable(entry_twfe))
entry_event_table$term <- rownames(entry_event_table)
rownames(entry_event_table) <- NULL

entry_event_table %>%
  filter(grepl("^year::[0-9]{4}:GBR$", term)) %>%
  mutate(event_year = sub("^year::", "", term),
         event_year = sub(":GBR$", "", event_year)) %>%
  select(event_year, Estimate, `Std. Error`, `Pr(>|t|)`) %>%
  kable()
```

# Assessment

This construction is feasible if:

- the complement of the 2010 affiliate stock produces a sizable number of "new" affiliates,
- the resulting entry panel has enough variation by country and year,
- and the coefficient can be interpreted as changes in new affiliate appearance after 2010.

This construction is imperfect if:

- the first observed year is not the true year of establishment,
- affiliate identifiers change over time,
- or the affiliate-level complement does not map cleanly into the country-industry entry setup used in the main paper.
