---
title: "OLS-TWFE Event Study: Entry and Exit Counts (Industry × Country × Year)"
author: "Ayumu Tanaka"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Purpose

This file produces simple **OLS-TWFE** event-study plots for **entry** and **exit** *counts* at the **industry × country × year** level, using:

- `03_data_output/EntryExit/N_affiliate_entry_exit.dta` (created in `Data14_Entry_Exit_Data.Rmd`)

The treated unit is the UK (`iso == "GBR"`). The reference (omitted) year is 2014, following the style used in `01_code/03_r/Tab2_Fig4.Rmd`.

# Packages

```{r load-packages}
library(tidyverse)
library(rio)
library(fixest)
```

# Load data

```{r load-data}
df <- rio::import("../../03_data_output/EntryExit/N_affiliate_entry_exit.dta")

df <- df %>%
  mutate(
    year = as.integer(year),
    FASector = as.integer(FASector),
    treated = (iso == "GBR"),
    unit = interaction(iso, FASector, drop = TRUE)
  ) %>%
  filter(year >= 2010, year <= 2020)

summary(df)
```

# Comparison groups

```{r comparison-groups}
eu_hi_iso <- c("AUT", "BEL", "DNK", "FIN", "FRA", "DEU", "IRL", "ITA", "LUX", "NLD", "SWE", "GBR")
noneu_hi_iso <- c("CAN", "AUS", "CHE", "KOR", "NZL")

df <- df %>%
  mutate(
    sample_HI = iso %in% eu_hi_iso,
    sample_ALL = iso %in% c(eu_hi_iso, noneu_hi_iso)
  )

table(df$sample_HI, useNA = "ifany")
table(df$sample_ALL, useNA = "ifany")
```

# OLS-TWFE event studies

## Entry counts

```{r es-entry-ols}
es_entry_ols_hi <- fixest::feols(
  N_entry_industry ~ i(year, treated, ref = 2014) | year + unit,
  data = df %>% filter(sample_HI),
  vcov = ~ iso
)
es_entry_ols_all <- fixest::feols(
  N_entry_industry ~ i(year, treated, ref = 2014) | year + unit,
  data = df %>% filter(sample_ALL),
  vcov = ~ iso
)

fixest::etable(es_entry_ols_hi, es_entry_ols_all)
```

## Exit counts

```{r es-exit-ols}
es_exit_ols_hi <- fixest::feols(
  N_exit_industry ~ i(year, treated, ref = 2014) | year + unit,
  data = df %>% filter(sample_HI),
  vcov = ~ iso
)
es_exit_ols_all <- fixest::feols(
  N_exit_industry ~ i(year, treated, ref = 2014) | year + unit,
  data = df %>% filter(sample_ALL),
  vcov = ~ iso
)

fixest::etable(es_exit_ols_hi, es_exit_ols_all)
```

# Event-study plots (two comparison groups)

```{r plot-es-ols, dpi = 300}
op <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))

fixest::iplot(
  list(Entry = es_entry_ols_hi, Exit = es_exit_ols_hi),
  pt.join = TRUE,
  main = "Brexit referendum: Entry vs Exit (count)",
  sub = "OLS-TWFE ES. Comparison: EU high-income. Ref. year = 2014. 1994–2022.",
  xlab = "Year"
)
legend("topleft", col = 1:2, pch = 10, cex = 0.8, lwd = 1, lty = 1:2,
       legend = c("Entry", "Exit"),
       title = "Outcome")

fixest::iplot(
  list(Entry = es_entry_ols_all, Exit = es_exit_ols_all),
  pt.join = TRUE,
  main = "Brexit referendum: Entry vs Exit (count)",
  sub = "OLS-TWFE ES. Comparison: all high-income. Ref. year = 2014. 1994–2022.",
  xlab = "Year"
)
legend("topleft", col = 1:2, pch = 10, cex = 0.8, lwd = 1, lty = 1:2,
       legend = c("Entry", "Exit"),
       title = "Outcome")

par(op)
```

## Optional: save as EPS (not required)

```{r save-eps, eval=FALSE}
postscript("../../04_tex/main/Fig4_entry_exit_count_ols.eps", horizontal = FALSE,
           width = 12, height = 6)

op <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))

fixest::iplot(
  list(Entry = es_entry_ols_hi, Exit = es_exit_ols_hi),
  pt.join = TRUE,
  main = "Brexit referendum: Entry vs Exit (count)",
  sub = "OLS-TWFE ES. Comparison: EU high-income. Ref. year = 2014. 1994–2022.",
  xlab = "Year"
)
legend("topleft", col = 1:2, pch = 10, cex = 0.8, lwd = 1, lty = 1:2,
       legend = c("Entry", "Exit"),
       title = "Outcome")

fixest::iplot(
  list(Entry = es_entry_ols_all, Exit = es_exit_ols_all),
  pt.join = TRUE,
  main = "Brexit referendum: Entry vs Exit (count)",
  sub = "OLS-TWFE ES. Comparison: all high-income. Ref. year = 2014. 1994–2022.",
  xlab = "Year"
)
legend("topleft", col = 1:2, pch = 10, cex = 0.8, lwd = 1, lty = 1:2,
       legend = c("Entry", "Exit"),
       title = "Outcome")

par(op)
dev.off()
```
