---
title: "The Worldwide Governance Indicators, 2023 Update"
author: "Ayumu Tanaka"
date: "2024-05-25"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


# The Worldwide Governance Indicators, 2023 Update

- The Worldwide Governance Indicators (WGI) are designed to assess broad patterns in perceptions of governance across countries and over time.

- The WGI aggregate data from more than 30 think tanks, international organizations, nongovernmental organizations, and private firms across the world.

- The WGI feature six aggregate governance indicators for over 200 countries and territories over the period 1996–2022:

  1. Voice and Accountability
  1. Political Stability and Absence of Violence/Terrorism
  1. Government Effectiveness
  1. Regulatory Quality
  1. Rule of Law
  1. Control of Corruption

- The WGI are based on a comprehensive review of over 30 data sources, including surveys of households, firms, and experts in the public, private, and nonprofit sectors.

- The WGI are available at the World Bank's website.
  - [https://www.worldbank.org/en/publication/worldwide-governance-indicators](https://www.worldbank.org/en/publication/worldwide-governance-indicators)
  -  [wgidataset-stata.zip](https://www.worldbank.org/content/dam/sites/govindicators/doc/wgidataset-stata.zip)


# Load the data

```{r}
library(rio)
WGI <- import("../unused_data_raw/wgidataset-stata/wgidataset.dta")
```

# Describe the data 

```{r}
library(gtsummary)
library(dplyr)
# Describe the data
WGI %>%
  select(-code) %>%
  select(-countryname) %>%
  tbl_summary()

```


# Select the necessary columns 

```{r}
# Keep code year pvr ger rqr rlr ccr
WGI <- WGI[, c("code", "year", "pvr", "ger", "rqr", "rlr", "ccr")]
```

# Write the data as CSV using `rio` package

```{r}
export(WGI, "../unused_output/WGI.rds")
```


# Distribution of the observations

```{r}
library(ggplot2)

# plot the distribution of the observations by year
WGI %>%
  group_by(year) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "Distribution of the observations by year",
       x = "Year",
       y = "Number of observations")
```


# Describe the data again

```{r}
library(gtsummary)
WGI %>%
  select(-code) %>%
  tbl_summary()
```


