---
title: "Geocoding affiliate location in the UK"
author: "Ayumu Tanaka"
date: "2024-05-29"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # do not cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


# Load the package

```{r load-package}
library(ggplot2)
library(tidyverse)
library(rio)

```

# Load the data

```{r load-data}
# Load the data
library(rio)
SHJP_JP_FA <- import("../unused_output/SHJP_JP_FA.rds")

# Subset of UK
SHJP_JP_FA_GBR <- subset(SHJP_JP_FA, iso == "GBR")

# Export as rds
rio::export(SHJP_JP_FA_GBR, "../unused_output/SHJP_JP_FA_GBR.rds")

```


# Data Cleaning before geo-coding

- Geocoding can be done at the Geoapify's free online tool:
  - https://www.geoapify.com/tools/geocoding-online/
- The data should be cleaned before geocoding.
- The data should be divided into 8 parts to avoid the limitation of the free online tool.


```{r data-cleaning}

library(tidyverse)
# Select variables related to the location
aff_GBR_address <- SHJP_JP_FA_GBR %>% 
  select(AffiliateCode, AffiliateNameAlph, JPCode, countryname, year, AddressAlph)

# Create address ID variable which is unique to AddressAlph
aff_GBR_address$address_id <- as.factor(as.numeric(as.factor(aff_GBR_address$AddressAlph)))

# Subset of the data with one obserbation per each address_id
aff_GBR_address_unique <- aff_GBR_address %>% 
  distinct(address_id, .keep_all = TRUE)

# Select variables
aff_GBR_address_unique <- aff_GBR_address_unique %>% 
  select(countryname, AddressAlph, address_id)

# Sort the data by address_id
aff_GBR_address_unique <- aff_GBR_address_unique %>% 
  arrange(address_id)

# Covert address_id to numeric
aff_GBR_address_unique$address_id <- as.numeric(as.character(aff_GBR_address_unique$address_id))

# Divide the data into 8 parts
aff_GBR_address_unique$group <- cut(aff_GBR_address_unique$address_id, breaks = 8, labels = FALSE)

# Export as csv by 8 group
for (i in 1:8) {
  aff_GBR_address_unique_i <- aff_GBR_address_unique %>% 
    filter(group == i)
  rio::export(aff_GBR_address_unique_i, paste0("../unused_output/aff_GBR_address_unique_", i, ".csv"))
}

# Export as csv
#rio::export(aff_GBR_address_unique, "../Data_output/aff_GBR_address_unique.csv")

```


# Load the output of Geocoding 

- The output of Geocoding should be loaded and merged with the original data.

```{r load-geocoding-output}
# Load the output of Geocoding for i =1:8

# Import the data
aff_GBR_address_geocoded_1 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_1_geocoded.csv")
aff_GBR_address_geocoded_2 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_2_geocoded.csv")
aff_GBR_address_geocoded_3 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_3_geocoded.csv")
aff_GBR_address_geocoded_4 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_4_geocoded.csv")
aff_GBR_address_geocoded_5 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_5_geocoded.csv")
aff_GBR_address_geocoded_6 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_6_geocoded.csv")
aff_GBR_address_geocoded_7 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_7_geocoded.csv")
aff_GBR_address_geocoded_8 <- import("../unused_data_raw/geocoded_data/aff_GBR_address_unique_8_geocoded.csv")


# Combine the data 1 to 4
aff_GBR_address_geocoded <- rbind(aff_GBR_address_geocoded_1,
                                  aff_GBR_address_geocoded_2, 
                                  aff_GBR_address_geocoded_3,
                                  aff_GBR_address_geocoded_4,
                                  aff_GBR_address_geocoded_5,
                                  aff_GBR_address_geocoded_6,
                                  aff_GBR_address_geocoded_7,
                                  aff_GBR_address_geocoded_8)


# Select the necessary columns
aff_GBR_address_geocoded <- aff_GBR_address_geocoded %>% 
  select(original_address_id, original_AddressAlph, lat, lon, city, county)  

# Count the NA of lat/lon
sum(is.na(aff_GBR_address_geocoded$lat))
sum(is.na(aff_GBR_address_geocoded$lon))


```


# Replace lot/lat for NA

- Replace the NA of lat/lon with the correct value.

```{r replace-lat-lon}
# Replace the NA of lat/lon with the correct value
## (1) 14 Blackhill Rd.West Holton Heath Trading Park Poole,Dorset,BHI6 6LF to 50.71752380203605, -2.073155041660397
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="14 Blackhill Rd.West Holton Heath Trading Park Poole,Dorset,BHI6 6LF"] <- 50.71752380203605
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="14 Blackhill Rd.West Holton Heath Trading Park Poole,Dorset,BHI6 6LF"] <- -2.073155041660397

## (2) 12 Erca Rd.Stacey Bushes Milton Keynes MK12 6HS to 52.05039, -0.79844930
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="12 Erca Rd.Stacey Bushes Milton Keynes MK12 6HS"] <- 52.05039
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="12 Erca Rd.Stacey Bushes Milton Keynes MK12 6HS"] <- -0.79844930
## city to Milton Keynes, county to Buckinghamshire
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="12 Erca Rd.Stacey Bushes Milton Keynes MK12 6HS"] <- "Milton Keynes"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="12 Erca Rd.Stacey Bushes Milton Keynes MK12 6HS"] <- "Buckinghamshire"

## (3) 1230 High Rd.Whetstone,London N.20 OLH to 51.60784,-0.34035160
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="1230 High Rd.Whetstone,London N.20 OLH"] <- 51.60784
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="1230 High Rd.Whetstone,London N.20 OLH"] <- -0.34035160
## London, Greater London
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="1230 High Rd.Whetstone,London N.20 OLH"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="1230 High Rd.Whetstone,London N.20 OLH"] <- "Greater London"

## (4) 12b Beehive 3,Lingfield Point,Darlington,Country Durham,DL1 1YN 
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="12b Beehive 3,Lingfield Point,Darlington,Country Durham,DL1 1YN"] <- "Darlington"

## (5) 2 Longwalk Rd.Hayes Park,Uxbridge Middlesex,UB11 1AB to 51.51039
#-0.44777603, London, Greater London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Hayes Park,Uxbridge Middlesex,UB11 1AB"] <- 51.51039
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Hayes Park,Uxbridge Middlesex,UB11 1AB"] <- -0.44777603
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Hayes Park,Uxbridge Middlesex,UB11 1AB"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Hayes Park,Uxbridge Middlesex,UB11 1AB"] <- "Greater London"

## (6) 2 Longwalk Rd.Stockley Park,Uxbridge,Middlesex UB11 1AB to 51.51039
#-0.44777603, London, Greater London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Stockley Park,Uxbridge,Middlesex UB11 1AB"] <- 51.51039
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Stockley Park,Uxbridge,Middlesex UB11 1AB"] <- -0.44777603
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Stockley Park,Uxbridge,Middlesex UB11 1AB"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="2 Longwalk Rd.Stockley Park,Uxbridge,Middlesex UB11 1AB"] <- "Greater London"

## (7). Aberdeen City belong to Aberdeenshire county
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$city=="Aberdeen City"] <- "Aberdeenshire"

## (8) 2-8 Honduras St.London EC1Y OTX to 51.52390, -0.09594700, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="2-8 Honduras St.London EC1Y OTX"] <- 51.52390
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="2-8 Honduras St.London EC1Y OTX"] <- -0.09594700
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="2-8 Honduras St.London EC1Y OTX"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="2-8 Honduras St.London EC1Y OTX"] <- "London"

## (9) 2nd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL to 51.49192019308762, -0.22188737394244676, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="2nd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- 51.49192019308762
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="2nd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- -0.22188737394244676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="2nd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="2nd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- "London"

## (10) 3rd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL to 51.49192019308762, -0.22188737394244676, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="3rd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- 51.49192019308762
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="3rd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- -0.22188737394244676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="3rd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="3rd Fl.,The Metro Bldg.,1 Butterwick,Hammersmith,London W6 8DL"] <- "London"

## (11) 47 Condvit St.Nl,London to 51.514284748842414, -0.12474993439392291, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="47 Condvit St.Nl,London"] <- 51.514284748842414
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="47 Condvit St.Nl,London"] <- -0.12474993439392291
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="47 Condvit St.Nl,London"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="47 Condvit St.Nl,London"] <- "London"

## (12) 4th Fl.Bow Bells House Bread St.London EC4M 9BQ to 51.51386, -0.09458930, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="4th Fl.Bow Bells House Bread St.London EC4M 9BQ"] <- 51.51386
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="4th Fl.Bow Bells House Bread St.London EC4M 9BQ"] <- -0.09458930
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="4th Fl.Bow Bells House Bread St.London EC4M 9BQ"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="4th Fl.Bow Bells House Bread St.London EC4M 9BQ"] <- "London"

## (13) 4th.Fl.Condor House,14 St.Paul's Churchyard,London EC4M 8BD to 51.51332338708703, -0.09984055092409298, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="4th.Fl.Condor House,14 St.Paul's Churchyard,London EC4M 8BD"] <- 51.51332338708703
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="4th.Fl.Condor House,14 St.Paul's Churchyard,London EC4M 8BD"] <- -0.09984055092409298
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="4th.Fl.Condor House,14 St.Paul's Churchyard,London EC4M 8BD"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="4th.Fl.Condor House,14 St.Paul's Churchyard,London EC4M 8BD"] <- "London"

## (14) 51 Spindus Rd.Speke Hall Ind.Estate,Liverpool L24 1YA to 53.34361, -2.86446860, Liverpool, Merseyside
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool L24 1YA"] <- 53.34361
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool L24 1YA"] <- -2.86446860
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool L24 1YA"] <- "Liverpool"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool L24 1YA"] <- "Merseyside"

## (15) 51 Spindus Rd.Speke Hall Ind.Estate,Liverpool,L24 1YA to 53.34361, -2.86446860, Liverpool, Merseyside
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool,L24 1YA"] <- 53.34361
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool,L24 1YA"] <- -2.86446860
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool,L24 1YA"] <- "Liverpool"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Ind.Estate,Liverpool,L24 1YA"] <- "Merseyside"

## (16) 51 Spindus Rd.Speke Hall Industrial Estate,Liverpool L24 1YA to 53.34361, -2.86446860, Liverpool, Merseyside
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Industrial Estate,Liverpool L24 1YA"] <- 53.34361
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Industrial Estate,Liverpool L24 1YA"] <- -2.86446860
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Industrial Estate,Liverpool L24 1YA"] <- "Liverpool"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="51 Spindus Rd.Speke Hall Industrial Estate,Liverpool L24 1YA"] <- "Merseyside"

## (17) 66 Chiltem St.London W1M 2AP to 51.52080, -0.15601200, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="66 Chiltem St.London W1M 2AP"] <- 51.52080
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="66 Chiltem St.London W1M 2AP"] <- -0.15601200
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="66 Chiltem St.London W1M 2AP"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="66 Chiltem St.London W1M 2AP"] <- "London"

## (18) 66 Chilten St.London W1M 2AP to 51.52080, -0.15601200, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London W1M 2AP"] <- 51.52080
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London W1M 2AP"] <- -0.15601200
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London W1M 2AP"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London W1M 2AP"] <- "London"

## (19) 66 Chilten St.London,W1M 2AP to 51.52080, -0.15601200, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London,W1M 2AP"] <- 51.52080
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London,W1M 2AP"] <- -0.15601200
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London,W1M 2AP"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="66 Chilten St.London,W1M 2AP"] <- "London"

## (20) 74-78 Finsbury Pavement,London EC 2A-1AT to 51.52012, -0.08733430, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="74-78 Finsbury Pavement,London EC 2A-1AT"] <- 51.52012
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="74-78 Finsbury Pavement,London EC 2A-1AT"] <- -0.08733430
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="74-78 Finsbury Pavement,London EC 2A-1AT"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="74-78 Finsbury Pavement,London EC 2A-1AT"] <- "London"

## (21) Beeswing House 31 Sheep St.Wellingborough Northants NN8 1BZ to 52.30040049048032, -0.6924170220443967, Wellingborough, Northamptonshire
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Beeswing House 31 Sheep St.Wellingborough Northants NN8 1BZ"] <- 52.30040049048032
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Beeswing House 31 Sheep St.Wellingborough Northants NN8 1BZ"] <- -0.6924170220443967
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Beeswing House 31 Sheep St.Wellingborough Northants NN8 1BZ"] <- "Wellingborough"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Beeswing House 31 Sheep St.Wellingborough Northants NN8 1BZ"] <- "Northamptonshire"

## (22) Burnastone,Derbyshire,DE1 9TA to 52.87269, -1.57399490, Derby, Derbyshire
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Burnastone,Derbyshire,DE1 9TA"] <- 52.87269
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Burnastone,Derbyshire,DE1 9TA"] <- -1.57399490
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Burnastone,Derbyshire,DE1 9TA"] <- "Derby"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Burnastone,Derbyshire,DE1 9TA"] <- "Derbyshire"

## (23) Condor House 14 St.Paul's Churchyard,London,EC4M 8BD to 51.51349100961623, -0.1000041604498566, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Condor House 14 St.Paul's Churchyard,London,EC4M 8BD"] <- 51.51349100961623
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Condor House 14 St.Paul's Churchyard,London,EC4M 8BD"] <- -0.1000041604498566
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Condor House 14 St.Paul's Churchyard,London,EC4M 8BD"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Condor House 14 St.Paul's Churchyard,London,EC4M 8BD"] <- "London"

## (24) Great Britian Olympus Park,Quedgeley Gloucester GL2 4NF to 51.8311176579963, -2.274196172070395
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester GL2 4NF"] <- 51.8311176579963
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester GL2 4NF"] <- -2.274196172070395
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester GL2 4NF"] <- "Gloucester"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester GL2 4NF"] <- "Gloucestershire"

## (25) Great Britian Olympus Park,Quedgeley Gloucester,GL2 4NF to 51.8311176579963, -2.274196172070395
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester,GL2 4NF"] <- 51.8311176579963
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester,GL2 4NF"] <- -2.274196172070395
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester,GL2 4NF"] <- "Gloucester"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Great Britian Olympus Park,Quedgeley Gloucester,GL2 4NF"] <- "Gloucestershire"

## (26) Hammersmith Int'l Centre,3 Shortlands,London,W6 8EE to 51.49270
# -0.21978825, London, London
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Hammersmith Int'l Centre,3 Shortlands,London,W6 8EE"] <- 51.49270
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Hammersmith Int'l Centre,3 Shortlands,London,W6 8EE"] <- -0.21978825
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Hammersmith Int'l Centre,3 Shortlands,London,W6 8EE"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Hammersmith Int'l Centre,3 Shortlands,London,W6 8EE"] <- "London"

## (27) Hunts.Rise,South Marston PK.Swindon,Wilts,SN3 4TW to 51.59807, -1.74055500
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Hunts.Rise,South Marston PK.Swindon,Wilts,SN3 4TW"] <- 51.59807
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Hunts.Rise,South Marston PK.Swindon,Wilts,SN3 4TW"] <- -1.74055500
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Hunts.Rise,South Marston PK.Swindon,Wilts,SN3 4TW"] <- "Swindon"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Hunts.Rise,South Marston PK.Swindon,Wilts,SN3 4TW"] <- "Wiltshire"

## (28) Jellicoe House Botleigh Grange,Hedge End,Southampton,SO3 4TX to 50.91543, -1.30714230
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Jellicoe House Botleigh Grange,Hedge End,Southampton,SO3 4TX"] <- 50.91543
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Jellicoe House Botleigh Grange,Hedge End,Southampton,SO3 4TX"] <- -1.30714230
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Jellicoe House Botleigh Grange,Hedge End,Southampton,SO3 4TX"] <- "Southampton"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Jellicoe House Botleigh Grange,Hedge End,Southampton,SO3 4TX"] <- "Hampshire"

## (29) La Motte Chambers St.Heliet,Jer sey,C.I.to 49.18447868869196, -2.100899977081222
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="La Motte Chambers St.Heliet,Jer sey,C.I."] <- 49.18447868869196
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="La Motte Chambers St.Heliet,Jer sey,C.I."] <- -2.100899977081222
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="La Motte Chambers St.Heliet,Jer sey,C.I."] <- "Jersey"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="La Motte Chambers St.Heliet,Jer sey,C.I."] <- "Jersey"

## (30) Lancashier to 54.05519102500022, -2.807323488877313
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Lancashier"] <- 54.05519102500022
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Lancashier"] <- -2.807323488877313
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Lancashier"] <- "Lancashire"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Lancashier"] <- "Lancashire"

## (31) Mouticello House,45 Rusell Sq.London WC1B 4JP to 51.520717567646635, -0.1259477162684768
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Mouticello House,45 Rusell Sq.London WC1B 4JP"] <- 51.520717567646635
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Mouticello House,45 Rusell Sq.London WC1B 4JP"] <- -0.1259477162684768
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Mouticello House,45 Rusell Sq.London WC1B 4JP"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Mouticello House,45 Rusell Sq.London WC1B 4JP"] <- "London"

## (32) P.O.Box 70 10th Fl.,Commercial Union Bldg.,St.Helen's.1-Undershaft,London EC3A 8JJ to 51.514409441192704, -0.08163365761782755
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="P.O.Box 70 10th Fl.,Commercial Union Bldg.,St.Helen's.1-Undershaft,London EC3A 8JJ"] <- 51.514409441192704
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="P.O.Box 70 10th Fl.,Commercial Union Bldg.,St.Helen's.1-Undershaft,London EC3A 8JJ"] <- -0.08163365761782755
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="P.O.Box 70 10th Fl.,Commercial Union Bldg.,St.Helen's.1-Undershaft,London EC3A 8JJ"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="P.O.Box 70 10th Fl.,Commercial Union Bldg.,St.Helen's.1-Undershaft,London EC3A 8JJ"] <- "London"

## (33) Part 9th Fl.CP House,97/107 Uxbridge Rd.Ealing,London W5 5TL to 51.51167584332843, -0.31278054510518477
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Part 9th Fl.CP House,97/107 Uxbridge Rd.Ealing,London W5 5TL"] <- 51.51167584332843
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Part 9th Fl.CP House,97/107 Uxbridge Rd.Ealing,London W5 5TL"] <- -0.31278054510518477
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Part 9th Fl.CP House,97/107 Uxbridge Rd.Ealing,London W5 5TL"] <- "London"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Part 9th Fl.CP House,97/107 Uxbridge Rd.Ealing,London W5 5TL"] <- "London"

## (34) Plastribution House 81 Market St.Ashby-de-la-Zouch,Leicestershire LE6 5AH to 52.74803046577447, -1.4694679315451427
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Plastribution House 81 Market St.Ashby-de-la-Zouch,Leicestershire LE6 5AH"] <- 52.74803046577447
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Plastribution House 81 Market St.Ashby-de-la-Zouch,Leicestershire LE6 5AH"] <- -1.4694679315451427
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Plastribution House 81 Market St.Ashby-de-la-Zouch,Leicestershire LE6 5AH"] <- "Ashby-de-la-Zouch"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Plastribution House 81 Market St.Ashby-de-la-Zouch,Leicestershire LE6 5AH"] <- "Leicestershire"

## (35) Prioslee Telford,Shropshire TF2 9NS to 52.68255, -2.41812000
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Prioslee Telford,Shropshire TF2 9NS"] <- 52.68255
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Prioslee Telford,Shropshire TF2 9NS"] <- -2.41812000
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Prioslee Telford,Shropshire TF2 9NS"] <- "Telford"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Prioslee Telford,Shropshire TF2 9NS"] <- "Shropshire"

## (36) Rutland House Pitt St.,St.Helier Jersey C.I. to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey C.I."] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey C.I."] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey C.I."] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey C.I."] <- "Jersey"

## (37) Rutland House Pitt St.,St.Helier Jersey. to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey."] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey."] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey."] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier Jersey."] <- "Jersey"

## (38) Rutland House Pitt St.,St.Helier,Jersey,Channel Islands to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier,Jersey,Channel Islands"] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier,Jersey,Channel Islands"] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier,Jersey,Channel Islands"] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House Pitt St.,St.Helier,Jersey,Channel Islands"] <- "Jersey"

## (39) Rutland House,Pitt St.,St.Helier Jersey Channel Islands to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey Channel Islands"] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey Channel Islands"] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey Channel Islands"] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey Channel Islands"] <- "Jersey"

## (40) Rutland House,Pitt St.,St.Helier Jersey.Channel Island to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey.Channel Island"] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey.Channel Island"] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey.Channel Island"] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Rutland House,Pitt St.,St.Helier Jersey.Channel Island"] <- "Jersey"

## (41) St.Helier,Jersey,Channel Islands to 49.18039484878236, -2.103169031473648
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="St.Helier,Jersey,Channel Islands"] <- 49.18039484878236
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="St.Helier,Jersey,Channel Islands"] <- -2.103169031473648
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="St.Helier,Jersey,Channel Islands"] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="St.Helier,Jersey,Channel Islands"] <- "Jersey"

## (42) Suite 17 Lomond House Almondvale Livingston,West Lothian EH 54,6QF to 55.88520666548146, -3.5081952101192044
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Suite 17 Lomond House Almondvale Livingston,West Lothian EH 54,6QF"] <- 55.88520666548146
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Suite 17 Lomond House Almondvale Livingston,West Lothian EH 54,6QF"] <- -3.5081952101192044
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Suite 17 Lomond House Almondvale Livingston,West Lothian EH 54,6QF"] <- "Livingston"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Suite 17 Lomond House Almondvale Livingston,West Lothian EH 54,6QF"] <- "West Lothian"

## (43) Timberham Hose,Gatwick Airport,West Sussex,RH6 0EQ to 51.158834161666874, -0.18432714512450585
# Gatwick's World Cargo Center, Timberham Way, Horley, Gatwick RH6 0EY, UK
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Timberham Hose,Gatwick Airport,West Sussex,RH6 0EQ"] <- 51.158834161666874
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Timberham Hose,Gatwick Airport,West Sussex,RH6 0EQ"] <- -0.18432714512450585
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Timberham Hose,Gatwick Airport,West Sussex,RH6 0EQ"] <- "Gatwick"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Timberham Hose,Gatwick Airport,West Sussex,RH6 0EQ"] <- "West Sussex"

## (44) Unit 11,Liddall Way Horton Rd.,West Drayton Middlesex,UB7 8PG to 51.50572, -0.47014660
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Unit 11,Liddall Way Horton Rd.,West Drayton Middlesex,UB7 8PG"] <- 51.50572
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Unit 11,Liddall Way Horton Rd.,West Drayton Middlesex,UB7 8PG"] <- -0.47014660
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Unit 11,Liddall Way Horton Rd.,West Drayton Middlesex,UB7 8PG"] <- "West Drayton"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Unit 11,Liddall Way Horton Rd.,West Drayton Middlesex,UB7 8PG"] <- "Middlesex"

## (45) Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs to 52.62140355793062, -1.6459069555912953
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs"] <- 52.62140355793062
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs"] <- -1.6459069555912953
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs"] <- "Tamworth"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs"] <- "Staffordshire"

## (46) Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU to 52.50026712292236, -0.647984950610445
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU"] <- 52.50026712292236
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU"] <- -0.647984950610445
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU"] <- "Corby"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU"] <- "Northamptonshire"

## (47) Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL to 52.38759861207766, -0.25713608923765385
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- 52.38759861207766
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- -0.25713608923765385
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- "Huntington"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- "Cambridgeshire"

## (48) Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL to 52.38759861207766, -0.25713608923765385
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- 52.38759861207766
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- -0.25713608923765385
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- "Huntington"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL"] <- "Cambridgeshire"


## (49) Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY to 52.31215177615965, -0.3795445953198574
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY"] <- 52.31215177615965
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY"] <- -0.3795445953198574
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY"] <- "Kimbolton"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY"] <- "Cambridgeshire"

## (50) Walthamavey Essex to 51.685551969707596, 0.027834924513882593
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_AddressAlph=="Walthamavey Essex"] <- 51.685551969707596
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_AddressAlph=="Walthamavey Essex"] <- 0.027834924513882593
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_AddressAlph=="Walthamavey Essex"] <- "Walthamavey"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_AddressAlph=="Walthamavey Essex"] <- "Essex"



# Count the NA of lat/lon
sum(is.na(aff_GBR_address_geocoded$lat))
sum(is.na(aff_GBR_address_geocoded$lon))



```



# Subset of NA

```{r}
# Subset of NA
aff_GBR_address_geocoded_NA <- aff_GBR_address_geocoded[is.na(aff_GBR_address_geocoded$lat),]

# List all rows
aff_GBR_address_geocoded_NA

```

# Replace NA with correct lat/lon



```{r}
## (1) Rutland House Pitt St.,St.Helier Jersey to 49.185615171218, -2.108479245230676
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==2953] <- 49.185615171218
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==2953] <- -2.108479245230676
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==2953] <- "St.Helier"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==2953] <- "Jersey"

## (2) Unit 19,Darwell Park Mica Close Amington Industrial Est.Nr.Tamworth,Staffs to 52.62140355793062, -1.6459069555912953
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3371] <- 52.62140355793062
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3371] <- -1.6459069555912953
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3371] <- "Tamworth"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3371] <- "Staffordshire"

## (3) Unit 205H Stafford House 8 Brakey Rd.Weldon North Ind.Estate Corby Northants NN17 1LU to 52.50026712292236, -0.647984950610445
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3402] <- 52.50026712292236
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3402] <- -0.647984950610445
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3402] <- "Corby"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3402] <- "Northamptonshire"

## (4) Unit 4/5 Sawfield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL to 52.38759861207766, -0.25713608923765385
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3477] <- 52.38759861207766
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3477] <- -0.25713608923765385
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3477] <- "Huntington"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3477] <- "Cambridgeshire"

## (5) Unit 4/5 Sawield House,Alconbury Hill,Alconbury Weston,Huntington Cambridgeshire,PE28 4JL to 52.38759861207766, -0.25713608923765385
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3478] <- 52.38759861207766
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3478] <- -0.25713608923765385
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3478] <- "Huntington"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3478] <- "Cambridgeshire"

## (6) Unit2,Aberafan Rd.Baglan Industrial Park,Port Talbot,West Glamorgan SA12 70J to 51.6125, -3.7833
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3618] <- 51.6125
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3618] <- -3.7833
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3618] <- "Port Talbot"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3618] <- "West Glamorgan"

## (7) Unite 27,Queensway Meadouws Industrial Estate,Newport,Gwent NP9 0SP to 51.5883, -2.9986
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3622] <- 51.5883
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3622] <- -2.9986
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3622] <- "Newport"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3622] <- "Gwent"

## (8) Units V1-V2 Grovemere Court,Bicton Rural Ind.Park,Kimbolton,Huntingdon Cambridgeshire,PE28 0EY to 52.31215177615965, -0.3795445953198574
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3644] <- 52.31215177615965
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3644] <- -0.3795445953198574
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3644] <- "Kimbolton"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3644] <- "Cambridgeshire"

## (9) Walthamavey Essex to 51.685551969707596, 0.027834924513882593
aff_GBR_address_geocoded$lat[aff_GBR_address_geocoded$original_address_id==3699] <- 51.685551969707596
aff_GBR_address_geocoded$lon[aff_GBR_address_geocoded$original_address_id==3699] <- 0.027834924513882593
aff_GBR_address_geocoded$city[aff_GBR_address_geocoded$original_address_id==3699] <- "Walthamavey"
aff_GBR_address_geocoded$county[aff_GBR_address_geocoded$original_address_id==3699] <- "Essex"


# Count the NA of lat/lon
sum(is.na(aff_GBR_address_geocoded$lat))
sum(is.na(aff_GBR_address_geocoded$lon))

```


# Export the geo-coded data

```{r}
# Export as rds
rio::export(aff_GBR_address_geocoded, "../unused_output/aff_GBR_address_geocoded.rds")
```


# Combine SHJP_JP_FA_GBR with geo-coded data

```{r}
# Combine SHJP_JP_FA_GBR with geo-coded data
aff_GBR_address <- merge(aff_GBR_address, 
                                 aff_GBR_address_geocoded,
                                 by.x="address_id", 
                                 by.y="original_address_id", 
                                 all.x=TRUE)

# Remove original_AddressAlph
aff_GBR_address$original_AddressAlph <- NULL

# count the number of aff_GBR_address$AddressAlph==""
sum((aff_GBR_address$AddressAlph==""))

# If aff_GBR_address$AddressAlph=="", then replace lat/lon with NA
aff_GBR_address$lat[aff_GBR_address$AddressAlph==""] <- NA
aff_GBR_address$lon[aff_GBR_address$AddressAlph==""] <- NA
aff_GBR_address$city[aff_GBR_address$AddressAlph==""] <- NA
aff_GBR_address$county[aff_GBR_address$AddressAlph==""] <- NA

```

# Combine SHJP_JP_FA_GBR with geo-coded data

```{r}
# Select necessary columns of aff_GBR_address
aff_GBR_address <- aff_GBR_address[,c("AffiliateCode", "year", "lat", "lon", "city", "county")]

# Combine SHJP_JP_FA_GBR with geo-coded data

SHJP_JP_FA_GBR <- merge(SHJP_JP_FA_GBR, 
                                 aff_GBR_address,
                                 by.x = c("AffiliateCode", "year"),
                                 by.y = c("AffiliateCode", "year"), 
                                 all.x=TRUE)

```

# Export the SHJP_JP_FA_GBR

```{r}
# Export as rds
rio::export(SHJP_JP_FA_GBR, "../unused_output/SHJP_JP_FA_GBR.rds")

```

# Remove all 
```{r}
rm(list=ls())

```
