---
title: "The World Bank's Doing Business Report"
author: "Ayumu Tanaka"
date: "2024-05-26"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: yes
---

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, # show R code
                      cache = FALSE, # cache results
                      message=FALSE, # show messages
                      warning=FALSE) # show warnings

```


# The World Bank's Doing Business Report


- The World Bank's Doing Business Report has published the ease of doing business rankings between 2004 and 2020.

- The Doing Business measured business regulations for local firms in 190 economies.

- However, the World Bank has decided to discontinue the Doing Business report, after data irregularities on Doing Business 2018 and 2020 were reported internally in June 2020.

- The Doing Business's complete historical data up to Doing Business 2020, revised to correct data irregularities are available at the World Bank's website.
  - [https://archive.doingbusiness.org/en/doingbusiness](https://archive.doingbusiness.org/en/doingbusiness)
  -  [Historical-data.dta](https://archive.doingbusiness.org/content/dam/misc/doingbusiness/db2020/Historical-data.dta)


# Load the data

```{r}
library(rio)
DB<- import("../unused_data_raw/WB_Doing_Business/Historical-data.dta")
```

# Describe the data 

```{r}
library(gtsummary)
library(dplyr)
# Describe the data
DB %>%
  select(-cod) %>%
  select(-economy) %>%
  tbl_summary()

```


# Select the necessary columns 

```{r}
# Display the names of columns
names(DB)
# Keep cod year startbustime 
DB <- DB[, c("cod", "dbyear", "startbustime", "taxestotal")]
# Rename "dbyear" to "year"
names(DB)[names(DB) == "dbyear"] <- "year"
```

# Write the data as CSV using `rio` package

```{r}
library(rio)
export(DB, "../unused_output/DB.rds")
```


# Distribution of the observations

```{r}
library(ggplot2)

# plot the distribution of the observations by year
DB %>%
  group_by(year) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "Distribution of the observations by year",
       x = "Year",
       y = "Number of observations")
```


# Describe the data again

```{r}
library(gtsummary)
DB %>%
  select(-cod) %>%
  tbl_summary()
```

